### 2022-04-27 paper/paper.tex
set up paper things

\documentclass[twocolumn, twocolappendix]{aastex631}
\received{\today}
\shorttitle{Detecting DCOs with LISA}
\graphicspath{{../figures/}}

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{wrapfig}
\usepackage[figuresright]{rotating}

% remove indents in footnotes
\usepackage[hang,flushmargin]{footmisc}

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}

% custom function for adding units
\makeatletter
\newcommand{\unit}[1]{%
    \,\mathrm{#1}\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{}}
\newcommand{\gobblenextarg}[1]{\,\mathrm{#1}\@ifnextchar\bgroup{\gobblenextarg}{}}
\makeatother

\begin{document}

\title{The NEOCP in the Era of LSST}

% affiliations
\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\newcommand{\UvA}{Anton Pannekoek Institute for Astronomy \& Grappa, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
\newcommand{\UW}{Department of Astronomy, University of Washington, Seattle, WA, 98195}

\author[0000-0001-6147-5761]{T. Wagg}
\affiliation{\UW}

\correspondingauthor{Tom Wagg}
\email{tomjwagg@gmail.com}

\begin{abstract}
    \input{sections/abstract.tex}
\end{abstract}

\keywords{gravitational waves, gravitational wave detectors, compact objects, stellar mass black holes, neutron stars, binary stars, stellar evolution, pulsars}

\section{Introduction} \label{sec:intro}
\input{sections/introduction.tex}

\section{Method} \label{sec:method}
\input{sections/methods.tex}

\section{Results} \label{sec:results}
\input{sections/results.tex}

\section{Discussion} \label{sec:discussion}
\input{sections/discussion.tex}

\section{Conclusion \& Summary} \label{sec:conclusion}
\input{sections/conclusion.tex}

\begin{acknowledgements}
    We'll thank some people here
\end{acknowledgements}

\software{}

\bibliographystyle{aasjournal}
\bibliography{paper}{}

% \restartappendixnumbering

% \allowdisplaybreaks
% \appendix
% \input{sections/appendix.tex}

\end{document}

### 2022-05-15 paper/paper.tex
start writing the methods

@@
 \received{\today}
-\shorttitle{Detecting DCOs with LISA}
-\graphicspath{{../figures/}}
+\shorttitle{NEOCP in LSST era}
+\graphicspath{{figures/}}
 
@@
 \newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
+\newcommand{\dig}{\texttt{digest2}}
 
@@
 % affiliations
-\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
-\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
-\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
-\newcommand{\UvA}{Anton Pannekoek Institute for Astronomy \& Grappa, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
 \newcommand{\UW}{Department of Astronomy, University of Washington, Seattle, WA, 98195}
@@
 \affiliation{\UW}
+
+\author[0000-0003-1996-9252]{M. Juric}
+\affiliation{\UW}
+
+\author{\dots more}
 
@@
 
-\keywords{gravitational waves, gravitational wave detectors, compact objects, stellar mass black holes, neutron stars, binary stars, stellar evolution, pulsars}
+\keywords{Near-Earth objects, Asteroids, Solar system, Small Solar System bodies, Surveys}
 
@@
 \begin{acknowledgements}
-    We'll thank some people here
+    Acknowledgements
 \end{acknowledgements}
 
-\software{}
+\software{\texttt{astroML} \citep{VanderPlas+2012,VanderPlas+2014}, \texttt{scipy} \citep{Virtanen+2020}}
 

### 2022-05-15 paper/sections/methods.tex
start writing the methods

In order to make predictions for the NEOCP in the era of LSST, we make simulated observations of a catalogue of solar system objects that takes into account currently known objects. We then use the \dig{} code to calculate NEO scores for each object and use these values to make predictions for the NEOCP. In the subsections below we explain each of these steps in more details.

\subsection{Hybrid Catalogue}
\subsection{Simulated Observations}
\subsection{\dig{} Score Calculation}
\subsection{LSST Discovery probability}
\todo{need to actually do this}

% \url{https://www.astroml.org/modules/generated/astroML.density_estimation.KNeighborsDensity.html#astroML.density_estimation.KNeighborsDensity}

% \url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.cKDTree.query.html#scipy.spatial.cKDTree.query}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{density_comparisons.png}
    \caption{A comparison of the density of MPCORB objects with those objects that were matched by our hybrid catalogue algorithm.}
\end{figure}

### 2022-05-15 paper/sections/methods.tex
progress on hybrid catalogue descriptions

@@
 
-\subsection{Hybrid Catalogue}
+\subsection{Hybrid Catalogue Pipeline}
+Most studies that make predictions for LSST use a synthetic catalogue of solar system objects that doesn't account for prior observations \needcite{}.
+In reality, we have already detected more than a million objects in the solar system and this number will continue to grow until LSST comes online.
+This means that, current predictions of detection rates will be inflated since a fraction of ``new'' detections may already be known.
+Therefore, for this paper we created ``hybrid'' catalogue that combines a synthetic catalogue with all known observations.
+
+We created the hybrid catalogue to be dynamic, such that we can run a single pipeline to merge in an updated version of \mpco{} as more objects are discovered in the time until LSST comes online.
+All code to reproduce this hybrid catalogue is open-source and available on GitHub\footnote{\url{https://github.com/dirac-institute/hybrid_sso_catalogue/tree/main/hybridcat/hybridcat}}.
+
+\subsubsection{Data preprocessing}
+For the synthetic catalogue of the solar system with we use \sss{}, the Pan-STARRS Synthetic Solar System Model \citep{Grav+2011}.
+We merge this synthetic catalogue with the latest version of \mpco{}\footnote{\url{https://minorplanetcenter.net//iau/MPCORB.html}}, a database of all currently known objects.
+
+We use \texttt{OpenOrb} \citep{Granvik+2009} to convert both catalogues to Cartesian coordinates and propagate all orbits until the same date.
+
+\subsubsection{Merging algorithm}
+The general idea for the merging algorithm is to inject each object from \mpco{} into \sss{}, replacing objects that are similar to those injected.
+An object's similarity is determined based on its position, $\va{x}$, velocity, $\va{v}$, and absolute magnitude (size), ${H}$.
+
+\subsubsection{Assessing quality of hybrid catalogue}
+
 \subsection{Simulated Observations}
@@
     \includegraphics[width=\columnwidth]{density_comparisons.png}
-    \caption{A comparison of the density of MPCORB objects with those objects that were matched by our hybrid catalogue algorithm.}
+    \caption{A comparison of the density of \mpco{} objects with those objects that were matched in \sss{} by our hybrid catalogue pipeline.}
 \end{figure}

### 2022-05-15 paper/sections/methods.tex
add merging algorithm details

@@
 This means that, current predictions of detection rates will be inflated since a fraction of ``new'' detections may already be known.
-Therefore, for this paper we created ``hybrid'' catalogue that combines a synthetic catalogue with all known observations.
+Therefore, for this paper we created ``hybrid'' catalogue that combines a synthetic catalogue with all known observations, whilst keeping the population distributions relatively unchanged.
 
@@
 An object's similarity is determined based on its position, $\va{x}$, velocity, $\va{v}$, and absolute magnitude (size), ${H}$.
+
+We split each catalogue into bins of absolute magnitude linearly spaced from $-2$ to $28$ and perform the merge algorithm on each bin separately.
+For each bin we build a K-D trees for both catalogues based on the positions ($x, y, z$) of objects.
+For every MPCORB object we query the S3M tree for the nearest $100$ objects up to a maximum distance of $0.1 \unit{AU}$, excluding any that have already been matched to a different real object.
+From these remaining nearest neighbours, we select the S3M object with the closest velocity as the matched object.
+If there were no remaining neighbours, either because no synthetic objects were nearby or because all nearby objects had already been matched, then we directly add this real object without replacing a synthetic one.
+
+To complete the merging process, we compile the matched object IDs and delete them from S3M. We then add the entirety of MPCORB to the remaining catalogue, resulting in a hybrid catalogue.
 

### 2022-05-15 paper/sections/methods.tex
talk about checks of hybrid, make lipsum grey

@@
 \subsubsection{Assessing quality of hybrid catalogue}
+It is essential that the underlying distributions of the hybrid catalogue do not differ significantly from S3M so that we still accurately reproduce the solar system.
+In Figure~\ref{fig:hybrid_vs_s3m_dists}, we show the distributions of the absolute magnitude and six orbital elements in both the hybrid catalogue and S3M.
+It is evident that the distributions are essentially identical.
+
+\begin{figure*}[htb]
+    \centering
+    \includegraphics[width=\textwidth]{hybrid_vs_s3m_distributions.png}
+    \caption{A comparison of the parameter distributions of S3M and the hybrid catalogue.}
+    \label{fig:hybrid_vs_s3m_dists}
+\end{figure*}
+
+As a further check, we compared MPCORB to the objects that were removed from S3M, since these should have nearly identical distributions.
+In Figure~\ref{fig:density_compare}, we show a comparison of the densities for the heliocentric $x$ and $y$ and it is clear that these distributions are left unchanged in the hybrid catalogue.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{density_comparisons.png}
+    \caption{A comparison of the density of \mpco{} objects with those objects that were matched in \sss{} by our hybrid catalogue pipeline.}
+    \label{fig:density_compare}
+\end{figure}
 
@@
 \subsection{LSST Discovery probability}
-\todo{need to actually do this}
-
-% \url{https://www.astroml.org/modules/generated/astroML.density_estimation.KNeighborsDensity.html#astroML.density_estimation.KNeighborsDensity}
-
-% \url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.cKDTree.query.html#scipy.spatial.cKDTree.query}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{density_comparisons.png}
-    \caption{A comparison of the density of \mpco{} objects with those objects that were matched in \sss{} by our hybrid catalogue pipeline.}
-\end{figure}
+\todo{}

### 2022-05-16 digest2/archive/0.223/src/223.f
digest2 shouldn't be in GitHub

@@ -1,2840 +1,0 @@
-
-      program digest2
-
-******************************************************************
-*
-* Digest2 is a Fortran code that determines the probability that 
-* an asteroid is of a particular dynamic class based on the sky
-* motion of the asteroid. The digest2 code is an amalgamation of
-* a Rob McNaught/David Asher code named Pangloss that determines
-* orbital elements for two astrometric positions and a bunch of
-* code by Carl Hergenrother that determines the probabilities that
-* an object is unusual and other assorted stuff. CWH 2002-03-19
-*
-******************************************************************
-
-******************************************************************
-* NOTE: Code in caps are McNaught/Asher code while lower case 
-*       lines are Hergenrother.
-******************************************************************
-
-      IMPLICIT NONE
-
-      LOGICAL FLAG
-      REAL*8 DAY,Q,E,JD1,DT,R
-      REAL*8 RA,W,N,I,XS,YS,ZS,ELONG,PSI,K,W1,N1,I1,W2,N2,I2
-      REAL*8 M1,TH,N0,mb_count,neo_count,h18n,score
-      REAL*8 LONG,DXY,DZ,A
-      REAL*8 RD,RSUN(2)
-      REAL*8 MEAN
-      REAL*8 EE(2,3),DD(0:2,3),DE,T(2)
-      REAL*8 O(3),V(3),D1,D2,TZ,DP,AL,T0,AA,BB,CC,U,SA,CA,ANG(2),AN
-      REAL*8 MAGOBS(2),HMAG,G,AET2M
-      REAL OBS(999,3),ET
-      INTEGER YEAR,MONTH,NUMBER,OBSCODE,IUNIT,IUOUT
-      INTEGER EPOCH,II,PARAB,ARC,NUMOBS,l,i3,i4
-      real semi1(20000),ecc1(20000),ncl1(20000)
-      real h6(20000),h7(20000),h8(20000),h9(20000),h10(20000)
-      real h11(20000),h12(20000),h13(20000),h14(20000),h15(20000)
[…]

### 2022-05-16 digest2/archive/01/digest2.f

@@ -1,992 +1,0 @@
-C
-C Digest2
-C
-C Copyright (c) 2005 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-C David Asher
-C
-C Permission is hereby granted, free of charge, to any person obtaining
-C a copy of this software and associated documentation files (the
-C "Software"), to deal in the Software without restriction, including
-C without limitation the rights to use, copy, modify, merge, publish,
-C distribute, sublicense, and/or sell copies of the Software, and to
-C permit persons to whom the Software is furnished to do so, subject
-C to the following conditions:
-C
-C The above copyright notice and this permission notice shall be
-C included in all copies or substantial portions of the Software.
-C
-C THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
-C EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
-C MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
-C IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
-C CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
-C TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
-C SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-
-      program digest2
-
-******************************************************************
-*
-* Digest2 is a Fortran code that determines the probability that 
-* an asteroid is of a particular dynamic class based on the sky
-* motion of the asteroid. The digest2 code is an amalgamation of
-* a Rob McNaught/David Asher code named Pangloss that determines
-* orbital elements for two astrometric positions and a bunch of
-* code by Carl Hergenrother that determines the probabilities that
-* an object is unusual and other assorted stuff. CWH 2002-03-19
-*
-******************************************************************
-
[…]

### 2022-05-16 digest2/archive/02/digest2.f90

@@ -1,1665 +1,0 @@
-!
-! Digest2
-!
-! Copyright (c) 2005 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-! David Asher
-!
-! Permission is hereby granted, free of charge, to any person obtaining
-! a copy of this software and associated documentation files (the
-! "Software"), to deal in the Software without restriction, including
-! without limitation the rights to use, copy, modify, merge, publish,
-! distribute, sublicense, and/or sell copies of the Software, and to
-! permit persons to whom the Software is furnished to do so, subject
-! to the following conditions:
-!
-! The above copyright notice and this permission notice shall be
-! included in all copies or substantial portions of the Software.
-!
-! THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
-! EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
-! MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
-! IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
-! CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
-! TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
-! SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-
-!=============================================================
-! Note:  The term 'NEO' used within this program really means any object
-! that the MPC would term 'unusual.' Currently that is not just q < 1.3
-! (NEOs) but also objects with e > .5 or i > 40.  Code dependent on this
-! definition is marked with the special comment word NEODEFSENSITIVE.
-
-!=============================================================
-! Module Hierarchy:
-!    main program
-!    mobject
-!    mdistance
-!    mangle
-!    bins
-!    morbit
-!    mconfig,mconstants,mbxaei,msve
-!
-! modules are in reverse order so that the source will compile
-! in a single pass
-
-!====================================================================
-module mconstants
-   !pi constants
-   real(8),parameter :: pi    = 3.14159265358979323846d0
-   real(8),parameter :: pi2   = pi*2d0
-   real(8),parameter :: drad  = pi/180d0
-   real(8),parameter :: radd  = 180d0/pi
-
[…]

### 2022-05-16 digest2/archive/03/d2math.c

@@ -1,548 +1,0 @@
-//! C99
-
-/* d2math.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2math.c
-
-the heart of digest2.  i/o, file formats, and so on are in other .c files.
-this file contains stuff like vector math, orbit calculations, and bin
-statistics.  "q" bin model is q, e, i, h, non-uniform bin spacing.
-*/
-
-#include <math.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05
-#define MAX_DISTANCE 100.
-
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-
-void initGlobals(void) {
-   // a little bit of one time setup 
-   K = .01720209895;
-   INV_K = 1. / K;
-   U = K * K;
-   TWO_PI = M_PI * 2.;
-
-   // Random numbers are used in aRange() in this file.  Linear congruential
-   // generator (LCG) code is here because library rand() has overhead from
-   // thread-safe stuff I don't need.  I use time(0) here to get a different
-   // seed for every program run, then rand() in the per-thread setup in
-   // main() (in digest2.c) to get a different LCG seed for each thread.
-   srand(time(0));
-   LCGA = pow(13, 13); // per NAG
-   LCGM = 1;
-   LCGM <<= 59;
-   invLCGM = 1. / LCGM;
-   LCGM--;
-}
-
-/* se2000
-
-solar ephemeris, J2000
-
-Args:
-   mjd
-
-Returns:
-   *psun_earth:  sun-earth vector in equatorial coordinates.
-   *psoe, *pcoe:  sine and cosine of ecciptic.
-
-Notes:
-   Approximate solar coordinates, per USNO.  Originally from
-   http://aa.usno.navy.mil/faq/docs/SunApprox.html, page now at
-   http://www.usno.navy.mil/USNO/astronomical-applications/
[…]

### 2022-05-16 digest2/archive/03/d2mpc.c

@@ -1,173 +1,0 @@
-//! C99
-
-/* mpc.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <ctype.h>
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-1999 on successful parse.
-   -1 on failure.
-*/
-int parseCod3(char *cod3) {
-   int hp;
-
-   if (isdigit(*cod3))
-      hp = *cod3 - '0';
-   else if (*cod3 >= 'A' && *cod3 <= 'J')
-      hp = *cod3 - 'A' + 10;
-   else
-      return -1;
-
-   if (isdigit(cod3[1]) && isdigit(cod3[2]))
-       return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-   return -1;
-}
-/* readMpcOcd()
-
-read obscode.dat into memory.
-
-Notes:
-   On error, prints message to stdout and terminates program.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
-   Converted here to circles for easier use later.
-*/
-void readMpcOcd(void) {
-    // Scale factor = earth radius in m / 1 AU in m.
-    const double sf = 6.37814e6 / 149.59787e9;
-
-    char *fn = "obscode.dat";
-    FILE *focd = fopen(fn, "r");
-    if (!focd)
-       fatal1(msgOpen, fn);
-
-    const int LINE_SIZE = 82;
-    char line[LINE_SIZE];
-    if (!fgets(line, LINE_SIZE, focd))
-       fatal1(msgRead, fn);
-
-    do {
-       int idx = parseCod3(line);
-       if (idx < 0)
-          continue;
-
-       double lon,rcos,rsin;
-       errno = 0;
-       line[30] = 0;
-       rsin = mustStrtod(line+21);
-       line[21] = 0;
-       rcos = mustStrtod(line+13);
-       line[13] = 0;
-       lon = mustStrtod(line+4);
-       if (errno)
-          continue;
-
-       site *ps = siteTable+idx;
-       ps->longitude = lon / 360.;
[…]

### 2022-05-16 digest2/archive/03/digest2.c

@@ -1,551 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-   // deadlock avoidance:
-   // a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
-// post-condition:  stage == 0
-pthread_cond_t cFree = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it returns a token to the ring
-// mutex: mRing
-// post-condition: ringFree > 0
-pthread_cond_t cDone = PTHREAD_COND_INITIALIZER;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-site siteTable[2000];
-int classConfig[D2CLASSES];
-int nClassConfig;
[…]

### 2022-05-16 digest2/archive/03/digest2.h

@@ -1,134 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-// observation.
-typedef struct {
-   double mjd;  // modified julian date
-   double ra;   // radians
-   double dec;
-   double vmag;  // observed magnitude, normalized to V band.
-                 // 0 means no magnitude.
-   int    site;  // index into site table.  basically an integer form of the
-                 // MPC three character obscode.
-} observation;
-
-// site.  observatory site parallax constants.
-typedef struct {
-   double longitude;  // unit is circles
-   double rhoCosPhi;  // unit is AU
-   double rhoSinPhi;
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-   INVALID,
-   UNPROC,
-   ACRON,
-   FAIL,
-   SUCCESS
-} tkstatus;
-
-typedef struct {
-   double rawScore;
-   double noIdScore;
-   _Bool  tagInClass[QX][EX][IX][HX];
-   _Bool  tagOutOfClass[QX][EX][IX][HX];
-   double sumAllInClass;
-   double sumUnkInClass;
-   double sumAllOutOfClass;
-   double sumUnkOutOfClass;
-   _Bool  dInClass[QX][EX][IX][HX];
-   _Bool  dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-   // these few elements really describe the tracklet
-   tkstatus status;
-   char desig[13];
-   observation *olist;
-   int obsCap; // allocated capacity of olist
-   int lines;  // for status=INVALID, this is the number of consecutive
-               // invalid lines.  otherwise, it is the number of valid
-               // observations in olist.
-
-   // distance independent working variables.  computed over the course
-   // of processing the tracklet.
[…]

### 2022-05-16 digest2/archive/04/d2math.c

@@ -1,553 +1,0 @@
-//! C99
-
-/* d2math.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2math.c
-
-the heart of digest2.  i/o, file formats, and so on are in other .c files.
-this file contains stuff like vector math, orbit calculations, and bin
-statistics.  "q" bin model is q, e, i, h, non-uniform bin spacing.
-*/
-
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05
-#define MAX_DISTANCE 100.
-
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-
-void initGlobals(void) {
-   // a little bit of one time setup 
-   K = .01720209895;
-   INV_K = 1. / K;
-   U = K * K;
-   TWO_PI = M_PI * 2.;
-
-   // Random numbers are used in aRange() in this file.  Linear congruential
-   // generator (LCG) code is here because library rand() has overhead from
-   // thread-safe stuff I don't need.  I use time(0) here to get a different
-   // seed for every program run, then rand() in the per-thread setup in
-   // main() (in digest2.c) to get a different LCG seed for each thread.
-   srand(time(0));
-   LCGA = pow(13, 13); // per NAG
-   LCGM = 1;
-   LCGM <<= 59;
-   invLCGM = 1. / LCGM;
-   LCGM--;
-}
-
-/* se2000
-
-solar ephemeris, J2000
-
-Args:
-   mjd
-
-Returns:
-   *psun_earth:  sun-earth vector in equatorial coordinates.
-   *psoe, *pcoe:  sine and cosine of ecciptic.
-
-Notes:
-   Approximate solar coordinates, per USNO.  Originally from
-   http://aa.usno.navy.mil/faq/docs/SunApprox.html, page now at
-   http://www.usno.navy.mil/USNO/astronomical-applications/
[…]

### 2022-05-16 digest2/archive/04/d2model.c

@@ -1,225 +1,0 @@
-//! C99
-
-/* d2model.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2model.c
-
-defines object classes available to digest2.  (where object and class are
-not oop terms.  object=solar system object, class=orbit classification.)
-*/
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double  modelAllSS    [QX][EX][IX][HX];
-double  modelUnkSS    [QX][EX][IX][HX];
-double  modelAllClass [D2CLASSES][QX][EX][IX][HX];
-double  modelUnkClass [D2CLASSES][QX][EX][IX][HX];
-
-double  qpart[QX] = { .4 ,  .7, .8,  .9, 1. , 1.1, 1.2, 1.3, 1.4, 1.5,
-                     1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3. , 3.2, 3.5,
-                     4.  , 4.5, 5., 5.5, 10., 20., 30., 40., 100.};
-double  epart[EX] = {.1, .2, .3, .4, .5, .7, .9, 1.1};
-double  ipart[IX] = {2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180};
-double  hpart[HX] = { 6,  8, 10, 11, 12, 13, 14, 15, 16, 17,
-                     18, 19, 20, 21, 22, 23, 24, 25.5};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]) {
-   return qeiToBin(q, e, i, bin) && hToBin(h, bin+3);
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3]) {
-   for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-      if (bin[0] == QX)
-         return 0;
-   for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
[…]

### 2022-05-16 digest2/archive/04/digest2.c

@@ -1,566 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-   // deadlock avoidance:
-   // a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
-// post-condition:  stage == 0
-pthread_cond_t cFree = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it returns a token to the ring
-// mutex: mRing
-// post-condition: ringFree > 0
-pthread_cond_t cDone = PTHREAD_COND_INITIALIZER;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-site siteTable[2000];
-int classConfig[D2CLASSES];
-int nClassConfig;
[…]

### 2022-05-16 digest2/archive/04/digest2.h

@@ -1,137 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-// observation.
-typedef struct {
-   double mjd;  // modified julian date
-   double ra;   // radians
-   double dec;
-   double vmag;  // observed magnitude, normalized to V band.
-                 // 0 means no magnitude.
-   int    site;  // index into site table.  basically an integer form of the
-                 // MPC three character obscode.
-   _Bool  spacebased;
-   double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants.
-typedef struct {
-   double longitude;  // unit is circles
-   double rhoCosPhi;  // unit is AU
-   double rhoSinPhi;
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-   INVALID,
-   UNPROC,
-   ACRON,
-   FAIL,
-   SUCCESS
-} tkstatus;
-
-typedef struct {
-   double rawScore;
-   double noIdScore;
-   _Bool  tagInClass[QX][EX][IX][HX];
-   _Bool  tagOutOfClass[QX][EX][IX][HX];
-   double sumAllInClass;
-   double sumUnkInClass;
-   double sumAllOutOfClass;
-   double sumUnkOutOfClass;
-   _Bool  dInClass[QX][EX][IX][HX];
-   _Bool  dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-   // these few elements really describe the tracklet
-   tkstatus status;
-   char desig[13];
-   observation *olist;
-   int obsCap; // allocated capacity of olist
-   int lines;  // for status=INVALID, this is the number of consecutive
-               // invalid lines.  otherwise, it is the number of valid
-               // observations in olist.
-
-   // distance independent working variables.  computed over the course
[…]

### 2022-05-16 digest2/archive/04/muk.c

@@ -1,275 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
--------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <stdio.h>
[…]

### 2022-05-16 digest2/archive/05/d2math.c

@@ -1,834 +1,0 @@
-//! C99
-
-/* d2math.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2math.c
-
-the heart of digest2.  i/o, file formats, and so on are in other .c files.
-this file contains stuff like vector math, orbit calculations, and bin
-statistics.  "q" bin model is q, e, i, h, non-uniform bin spacing.
-*/
-
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05
-#define MAX_DISTANCE 100.
-
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-
-void initGlobals(void) {
-   // a little bit of one time setup 
-   K = .01720209895;
-   INV_K = 1. / K;
-   U = K * K;
-   TWO_PI = M_PI * 2.;
-   arcsecrad = M_PI / (180 * 3600);
-   rtol = arcsecrad;
-
-   // Random numbers are used in aRange() in this file.  Linear congruential
-   // generator (LCG) code is here because library rand() has overhead from
-   // thread-safe stuff I don't need.  I use time(0) here to get a different
-   // seed for every program run, then rand() in the per-thread setup in
-   // main() (in digest2.c) to get a different LCG seed for each thread.
-   srand(time(0));
-   LCGA = pow(13, 13); // per NAG
-   LCGM = 1;
-   LCGM <<= 59;
-   invLCGM = 1. / LCGM;
-   LCGM--;
-}
-
-/* se2000
-
-solar ephemeris, J2000
-
-Args:
-   mjd
-
-Returns:
-   *psun_earth:  sun-earth vector in equatorial coordinates.
-   *psoe, *pcoe:  sine and cosine of ecciptic.
-
-Notes:
-   Approximate solar coordinates, per USNO.  Originally from
-   http://aa.usno.navy.mil/faq/docs/SunApprox.html, page now at
[…]

### 2022-05-16 digest2/archive/05/d2model.c

@@ -1,226 +1,0 @@
-//! C99
-
-/* d2model.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2model.c
-
-defines object classes available to digest2.  (where object and class are
-not oop terms.  object=solar system object, class=orbit classification.)
-*/
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double  modelAllSS    [QX][EX][IX][HX];
-double  modelUnkSS    [QX][EX][IX][HX];
-double  modelAllClass [D2CLASSES][QX][EX][IX][HX];
-double  modelUnkClass [D2CLASSES][QX][EX][IX][HX];
-
-double  qpart[QX] = { .4 ,  .7, .8,  .9, 1. , 1.1, 1.2, 1.3, 1.4, 1.5,
-                     1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3. , 3.2, 3.5,
-                     4.  , 4.5, 5., 5.5, 10., 20., 30., 40., 100.};
-double  epart[EX] = {.1, .2, .3, .4, .5, .7, .9, 1.1};
-double  ipart[IX] = {2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180};
-double  hpart[HX] = { 6,  8, 10, 11, 12, 13, 14, 15, 16, 17,
-                     18, 19, 20, 21, 22, 23, 24, 25.5};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]) {
-   return qeiToBin(q, e, i, bin) && hToBin(h, bin+3);
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3]) {
-   for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-      if (bin[0] == QX)
-         return 0;
-   for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
-      if (bin[1] == EX)
[…]

### 2022-05-16 digest2/archive/05/digest2.c

@@ -1,584 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-   // deadlock avoidance:
-   // a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
-// post-condition:  stage == 0
-pthread_cond_t cFree = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it returns a token to the ring
-// mutex: mRing
-// post-condition: ringFree > 0
-pthread_cond_t cDone = PTHREAD_COND_INITIALIZER;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-site siteTable[2000];
-int classConfig[D2CLASSES];
-int nClassConfig;
-_Bool classPossible;
[…]

### 2022-05-16 digest2/archive/05/gcf.h

@@ -1,45 +1,0 @@
-//! C99
-
-/* gcf.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323
-#endif
-
-typedef struct {
-   // various intermediate values, useful for generating statistics after
-   // the fit is done
-   int    nObs;
-   double mRot[3][3]; // rotation matrix
-   double ra0;        // ra offset
-   double (*rs)[2];   // rotated ra and dec
-   double t0;         // time offset
-   double *ntime;     // normalized times
-   // fit solution parameters
-   double r0;
-   double rr;
-   double d0;
-   double dr;
-} gcfparam;
-
-void gcFit(gcfparam *gcf, double mjd[], double sphr[][2]);
-
-// three variations of result functions:
-
-// compute an arbitrary position on the fitted great circle
-void gcPos(gcfparam *gcf, double t, double *ra, double *dec);
-
-// compute residuals in ra and dec.
-void gcRes(gcfparam *gcf, double res[][2]);
-
-// compute residuals in ra and dec, and the 2d rms.
-double gcRmsRes(gcfparam *gcf, double res[][2]);
-
-// compute 2d rms of residuals, don't bother to return residuals
-double gcRms(gcfparam *gcf);
-

### 2022-05-16 digest2/archive/05/gcr.c

@@ -1,201 +1,0 @@
-//! C99
-
-/* gcr.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <errno.h>
-#include <limits.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-
-#include "gcf.h"
-
-typedef struct {
-   double mjd;
-   double ra;
-   double dec;
-   double mag;
-} observation;
-
-typedef struct {
-   int nObs;
-   int oCap;
-   observation *olist;
-} tracklet;
-
-/* mustStrtod
-
-for required fields.  a version of atof that sets errno on blank input.
-also allows whitespace after sign
-*/
-double mustStrtod(char *str) {
-   char *endp;
-   _Bool neg = *str == '-';
-   if (neg || *str == '+')
-      str++;
-   double result = strtod(str, &endp);
-   if (!errno && endp == str)
-      errno = EINVAL;
-   return neg ? -result : result;
-}
-
-/* mustStrtoi
-
-returns int but actually disallows negatives.
-*/
-int mustStrtoi(char *str) {
-   char *endp;
-   long result = strtol(str, &endp, 10);
-   if (!errno)
-      if (endp == str || result < 0 || result > INT_MAX)
-         errno = EINVAL;
-   return result;
-}
-
-_Bool parseMpc80(char *line, observation *obsp) {
-   if (line[14] != 'C' && line[14] != 'S')
-      return 0;
-   // parse right to left so we can punch line with zeros as needed
-   line[70] = 0;
-   errno = 0;
-   // strtod meets our needs here to return 0 without error on blank input
-   obsp->mag = strtod(line+65, 0);
-   line[56] = 0;
-   // other fields are required.  use mustStrtod.
-   double decs = mustStrtod(line+51);
-   line[50] = 0;
-   int decm = mustStrtoi(line+48);
-   line[47] = 0;
-   int decd = mustStrtoi(line+45);
-   char decg = line[44];
-   line[44] = 0;
-   double ras = mustStrtod(line+38);
-   line[37] = 0;
-   int ram = mustStrtoi(line+35);
-   line[34] = 0;
-   int rah = mustStrtoi(line+32);
-   line[32] = 0;
-   double day = mustStrtod(line+23);
[…]

### 2022-05-16 digest2/archive/06/d2model.h

@@ -1,40 +1,0 @@
-//! C99
-
-/* d2model.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-// extents for model
-#define D2CLASSES 13
-#define QX 29
-#define EX 8
-#define IX 11
-#define HX 18
-
-// model
-extern double  modelAllSS    [QX][EX][IX][HX];
-extern double  modelUnkSS    [QX][EX][IX][HX];
-extern double  modelAllClass [D2CLASSES][QX][EX][IX][HX];
-extern double  modelUnkClass [D2CLASSES][QX][EX][IX][HX];
-
-// partition arrays
-extern double  qpart[QX];
-extern double  epart[EX];
-extern double  ipart[IX];
-extern double  hpart[HX];
-
-typedef _Bool (*classtest)(double, double, double);
-
-extern char *classAbbr[D2CLASSES];
-extern char *classHeading[D2CLASSES];
-extern classtest isClass[D2CLASSES];
-
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]);
-_Bool qeiToBin(double q, double e, double i, int bin[3]);
-_Bool hToBin(double h, int *ih);
-

### 2022-05-16 digest2/archive/06/digest2.c

@@ -1,584 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-   // deadlock avoidance:
-   // a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
-// post-condition:  stage == 0
-pthread_cond_t cFree = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it returns a token to the ring
-// mutex: mRing
-// post-condition: ringFree > 0
-pthread_cond_t cDone = PTHREAD_COND_INITIALIZER;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-site siteTable[2000];
-int classConfig[D2CLASSES];
-int nClassConfig;
-_Bool classPossible;
[…]

### 2022-05-16 digest2/archive/06/digest2.h

@@ -1,154 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-// observation.
-typedef struct {
-   double mjd;  // modified julian date
-   double ra;   // radians
-   double dec;
-   double vmag;  // observed magnitude, normalized to V band.
-                 // 0 means no magnitude.
-   int    site;  // index into site table.  basically an integer form of the
-                 // MPC three character obscode.
-   _Bool  spacebased;
-   double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants.
-typedef struct {
-   double longitude;  // unit is circles
-   double rhoCosPhi;  // unit is AU
-   double rhoSinPhi;
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-   INVALID,
-   UNPROC,
-   ACRON,
-   FAIL,
-   SUCCESS
-} tkstatus;
-
-typedef struct {
-   double rawScore;
-   double noIdScore;
-   _Bool  tagInClass[QX][EX][IX][HX];
-   _Bool  tagOutOfClass[QX][EX][IX][HX];
-   double sumAllInClass;
-   double sumUnkInClass;
-   double sumAllOutOfClass;
-   double sumUnkOutOfClass;
-   _Bool  dInClass[QX][EX][IX][HX];
-   _Bool  dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-   // these few elements really describe the tracklet
-   tkstatus status;
-   char desig[13];
-   observation *olist;
-   int obsCap; // allocated capacity of olist
-   int lines;  // for status=INVALID, this is the number of consecutive
-               // invalid lines.  otherwise, it is the number of valid
-               // observations in olist.
-
-   // distance independent working variables.  computed over the course
[…]

### 2022-05-16 digest2/archive/06/gcfmath.c

@@ -1,318 +1,0 @@
-//! C99
-
-/* gcfmath.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-gcfmath.c
-
-Math for great circle fit and residual calculator.  Input is observation
-triples of time, RA, and Dec.  Code here least-squares fits a great circle
-to RA and Dec with time as the independent variable.  It also computes
-residuals and an RMS of the residuals.
-*/
-
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-
-#include "gcf.h"
-
-const double TWO_PI = 2 * M_PI;
-
-// one arc second, in radians;
-const double arcsecrad = M_PI / (180 * 3600);
-
-// rotation tolerance = 1 arc sec.  roughly, if I rotate something and
-// it doesn't end up within an arc second of where I expect, there's a
-// problem.
-const double rtol = M_PI / (180 * 3600);
-
-/* dot3
-
-vector dot product
-*/
-double dot3(double a1[3], double a2[3]) {
-   return a1[0]*a2[0] + a1[1]*a2[1] + a1[2]*a2[2];
-}
-
-/* cross3
-
-vector cross product
-
-Args:
-   a, b:  three element vectors of double
-
-Returns:
-   a x b
-*/
-void cross3(double result[3], double a[3], double b[3]) {
-   result[0] = a[1]*b[2] - a[2]*b[1];
-   result[1] = a[2]*b[0] - a[0]*b[2];
-   result[2] = a[0]*b[1] - a[1]*b[0];
-} 
-
-/* dSphr2Cart
-
-Spherical (RA, Dec, in radians) to Cartesian (X, Y, Z unit vector)
-
-operates on arrays of coordinate tuples.
-first parameter is length of arrays.
-*/
-void dSphr2Cart(int len, double s[len][2], double c[len][3]) {
-   for (int i = 0; i < len; i++) {
-      double t = cos(s[i][1]);
-      c[i][0] = t * cos(s[i][0]);
-      c[i][1] = t * sin(s[i][0]);
-      c[i][2] = sin(s[i][1]);
-   }
-}
-
[…]

### 2022-05-16 digest2/archive/07/d2math.c

@@ -1,833 +1,0 @@
-//! C99
-
-/* d2math.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2math.c
-
-the heart of digest2.  i/o, file formats, and so on are in other .c files.
-this file contains stuff like vector math, orbit calculations, and bin
-statistics.  "q" bin model is q, e, i, h, non-uniform bin spacing.
-*/
-
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05
-#define MAX_DISTANCE 100.
-
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-
-void initGlobals(void) {
-   // a little bit of one time setup 
-   K = .01720209895;
-   INV_K = 1. / K;
-   U = K * K;
-   TWO_PI = M_PI * 2.;
-   arcsecrad = M_PI / (180 * 3600);
-   rtol = arcsecrad;
-
-   // Random numbers are used in aRange() in this file.  Linear congruential
-   // generator (LCG) code is here because library rand() has overhead from
-   // thread-safe stuff I don't need.  I use time(0) here to get a different
-   // seed for every program run, then rand() in the per-thread setup in
-   // main() (in digest2.c) to get a different LCG seed for each thread.
-   srand(time(0));
-   LCGA = pow(13, 13); // per NAG
-   LCGM = 1;
-   LCGM <<= 59;
-   invLCGM = 1. / LCGM;
-   LCGM--;
-}
-
-/* se2000
-
-solar ephemeris, J2000
-
-Args:
-   mjd
-
-Returns:
-   *psun_earth:  sun-earth vector in equatorial coordinates.
-   *psoe, *pcoe:  sine and cosine of ecciptic.
-
-Notes:
-   Approximate solar coordinates, per USNO.  Originally from
-   http://aa.usno.navy.mil/faq/docs/SunApprox.html, page now at
[…]

### 2022-05-16 digest2/archive/07/d2model.c

@@ -1,247 +1,0 @@
-//! C99
-
-/* d2model.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2model.c
-
-defines object classes available to digest2.  (where object and class are
-not oop terms.  object=solar system object, class=orbit classification.)
-*/
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double  modelAllSS    [QX][EX][IX][HX];
-double  modelUnkSS    [QX][EX][IX][HX];
-double  modelAllClass [D2CLASSES][QX][EX][IX][HX];
-double  modelUnkClass [D2CLASSES][QX][EX][IX][HX];
-
-double  qpart[QX] = { .4 ,  .7, .8,  .9, 1. , 1.1, 1.2, 1.3, 1.4, 1.5,
-                     1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3. , 3.2, 3.5,
-                     4.  , 4.5, 5., 5.5, 10., 20., 30., 40., 100.};
-double  epart[EX] = {.1, .2, .3, .4, .5, .7, .9, 1.1};
-double  ipart[IX] = {2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180};
-double  hpart[HX] = { 6,  8, 10, 11, 12, 13, 14, 15, 16, 17,
-                     18, 19, 20, 21, 22, 23, 24, 25.5};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]) {
-   _Bool r;
-   if ((r = qeiToBin(q, e, i, bin)))
-      bin[3] = hToBin(h);
-   return r;
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3]) {
-   for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-      if (bin[0] == QX)
-         return 0;
-   for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
[…]

### 2022-05-16 digest2/archive/07/d2mpc.c

@@ -1,200 +1,0 @@
-//! C99
-
-/* mpc.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <ctype.h>
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-1999 on successful parse.
-   -1 on failure.
-*/
-int parseCod3(char *cod3) {
-   int hp;
-
-   if (isdigit(*cod3))
-      hp = *cod3 - '0';
-   else if (*cod3 >= 'A' && *cod3 <= 'J')
-      hp = *cod3 - 'A' + 10;
-   else
-      return -1;
-
-   if (isdigit(cod3[1]) && isdigit(cod3[2]))
-       return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-   return -1;
-}
-/* readMpcOcd()
-
-read obscode.dat into memory.
-
-Notes:
-   On error, prints message to stdout and terminates program.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
-   Converted here to circles for easier use later.
-*/
-void readMpcOcd(void) {
-    // Scale factor = earth radius in m / 1 AU in m.
-    const double sf = 6.37814e6 / 149.59787e9;
-
-    char *fn = "obscode.dat";
-    FILE *focd = fopen(fn, "r");
-    if (!focd)
-       fatal1(msgOpen, fn);
-
-    const int LINE_SIZE = 82;
-    char line[LINE_SIZE];
-    if (!fgets(line, LINE_SIZE, focd))
-       fatal1(msgRead, fn);
-
-    do {
-       int idx = parseCod3(line);
-       if (idx < 0)
-          continue;
-
-       double lon,rcos,rsin;
-       errno = 0;
-       line[30] = 0;
-       rsin = mustStrtod(line+21);
-       line[21] = 0;
-       rcos = mustStrtod(line+13);
-       line[13] = 0;
-       lon = mustStrtod(line+4);
-       if (errno)
-          continue;
-
-       site *ps = siteTable+idx;
[…]

### 2022-05-16 digest2/archive/07/digest2.c

@@ -1,584 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-   // deadlock avoidance:
-   // a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
-// post-condition:  stage == 0
-pthread_cond_t cFree = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it returns a token to the ring
-// mutex: mRing
-// post-condition: ringFree > 0
-pthread_cond_t cDone = PTHREAD_COND_INITIALIZER;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-site siteTable[2000];
-int classConfig[D2CLASSES];
-int nClassConfig;
-_Bool classPossible;
[…]

### 2022-05-16 digest2/archive/07/gcr.c

@@ -1,319 +1,0 @@
-//! C99
-
-/* gcr.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-// POSIX for getopt()
-#define _POSIX_C_SOURCE 2
-
-#include <errno.h>
-#include <limits.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "gcf.h"
-
-#define LINE_SIZE 83
-
-typedef struct {
-   char   line[LINE_SIZE];
-   char   line2[LINE_SIZE];
-   char   desig[13];
-   double mjd;
-   double ra;
-   double dec;
-   double mag;
-} observation;
-
-typedef struct {
-   int nObs;
-   int oCap;
-   observation *olist;
-} tracklet;
-
-char *msgOpen = "Open %s failed.\n";
-char *msgRead = "Read %s failed.\n";
-char *msgWrite = "Write %s failed.\n";
-char *msgMemory = "Memory allocation failed.";
-char *msgUsage = "Usage:  gcr [options] <obsfile>\n\
-Options:\n\
-   -c <rms cutoff>  -- set cutoff, in arc seconds.\n\
-   -p <pass file>   -- create file with tracklets with rms < cutoff.\n\
-   -f <fail file>   -- create file with tracklets with rms >= cutoff.\n\
-   -q               -- quiet.  supress normal output.\n\
-   -h               -- print program help.";
-char *msgHelp = "\n\
-Obsfile is required and must be a file of 80 column MPC format observations.\n\
-By default, statistics are printed to stdout.  If any of the options\n\
--c -p -f or -q are used, pass file and fail file are created.  Valid\n\
-tracklets in the input are copied into one of the two files depending on\n\
-the computed rms.";
-
-_Bool split;
-_Bool quiet;
-double rmsCutoff;
-char *passFile;
-char *failFile;
-FILE *fpass;
-FILE *ffail;
-
-void fatal(char *msg) {
-   puts(msg);
-   exit(-1);
-}
-
-void fatal1(char *msg, char *arg) {
-   printf(msg, arg);
-   exit(-1);
-}
-
-/* mustStrtod
-
-for required fields.  a version of atof that sets errno on blank input.
-also allows whitespace after sign
-*/
-double mustStrtod(char *str) {
[…]

### 2022-05-16 digest2/archive/07/muk.c

@@ -1,275 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
--------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <stdio.h>
[…]

### 2022-05-16 digest2/archive/08/d2math.c

@@ -1,832 +1,0 @@
-//! C99
-
-/* d2math.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2math.c
-
-the heart of digest2.  i/o, file formats, and so on are in other .c files.
-this file contains stuff like vector math, orbit calculations, and bin
-statistics.  "q" bin model is q, e, i, h, non-uniform bin spacing.
-*/
-
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05
-#define MAX_DISTANCE 100.
-
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-
-void initGlobals(void) {
-   // a little bit of one time setup 
-   K = .01720209895;
-   INV_K = 1. / K;
-   U = K * K;
-   TWO_PI = M_PI * 2.;
-   arcsecrad = M_PI / (180 * 3600);
-   rtol = arcsecrad;
-
-   // Random numbers are used in aRange() in this file.  Linear congruential
-   // generator (LCG) code is here because library rand() has overhead from
-   // thread-safe stuff I don't need.  I use time(0) here to get a different
-   // seed for every program run, then rand() in the per-thread setup in
-   // main() (in digest2.c) to get a different LCG seed for each thread.
-   srand(time(0));
-   LCGA = pow(13, 13); // per NAG
-   LCGM = 1;
-   LCGM <<= 59;
-   invLCGM = 1. / LCGM;
-   LCGM--;
-}
-
-/* se2000
-
-solar ephemeris, J2000
-
-Args:
-   mjd
-
-Returns:
-   *psun_earth:  sun-earth vector in equatorial coordinates.
-   *psoe, *pcoe:  sine and cosine of ecciptic.
-
-Notes:
-   Approximate solar coordinates, per USNO.  Originally from
-   http://aa.usno.navy.mil/faq/docs/SunApprox.html, page now at
[…]

### 2022-05-16 digest2/archive/08/digest2.c

@@ -1,766 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-   {"help",    no_argument, 0, 'h'},
-   {"version", no_argument, 0, 'v'},
-   {"config",      required_argument, 0, 'c'},
-   {"model",       required_argument, 0, 'm'},
-   {"obscodes",    required_argument, 0, 'o'},
-   {"config-path", required_argument, 0, 'p'},
-   {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
[…]

### 2022-05-16 digest2/archive/08/muk.c

@@ -1,305 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
--------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <math.h>
[…]

### 2022-05-16 digest2/archive/09/d2math.c

@@ -1,837 +1,0 @@
-//! C99
-
-/* d2math.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2math.c
-
-the heart of digest2.  i/o, file formats, and so on are in other .c files.
-this file contains stuff like vector math, orbit calculations, and bin
-statistics.  "q" bin model is q, e, i, h, non-uniform bin spacing.
-*/
-
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05 // AU
-#define MAX_DISTANCE 100. // AU
-#define minDistanceStep .2 // AU
-#define minAngleStep .1 // radian
-#define ageLimit 2
-
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-
-void initGlobals(void) {
-   // a little bit of one time setup 
-   K = .01720209895;
-   INV_K = 1. / K;
-   U = K * K;
-   TWO_PI = M_PI * 2.;
-   arcsecrad = M_PI / (180 * 3600);
-   rtol = arcsecrad;
-
-   // Random numbers are used in aRange() in this file.  Linear congruential
-   // generator (LCG) code is here because library rand() has overhead from
-   // thread-safe stuff I don't need.  I use time(0) here to get a different
-   // seed for every program run, then rand() in the per-thread setup in
-   // main() (in digest2.c) to get a different LCG seed for each thread.
-   srand(time(0));
-   LCGA = pow(13, 13); // per NAG
-   LCGM = 1;
-   LCGM <<= 59;
-   invLCGM = 1. / LCGM;
-   LCGM--;
-}
-
-/* se2000
-
-solar ephemeris, J2000
-
-Args:
-   mjd
-
-Returns:
-   *psun_earth:  sun-earth vector in equatorial coordinates.
-   *psoe, *pcoe:  sine and cosine of ecciptic.
-
-Notes:
[…]

### 2022-05-16 digest2/archive/09/d2mpc.c

@@ -1,199 +1,0 @@
-//! C99
-
-/* mpc.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <ctype.h>
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-1999 on successful parse.
-   -1 on failure.
-*/
-int parseCod3(char *cod3) {
-   int hp;
-
-   if (isdigit(*cod3))
-      hp = *cod3 - '0';
-   else if (*cod3 >= 'A' && *cod3 <= 'J')
-      hp = *cod3 - 'A' + 10;
-   else
-      return -1;
-
-   if (isdigit(cod3[1]) && isdigit(cod3[2]))
-       return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-   return -1;
-}
-/* readMpcOcd()
-
-read obscode.dat into memory.
-
-Notes:
-   On error, prints message to stdout and terminates program.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
-   Converted here to circles for easier use later.
-*/
-void readMpcOcd(void) {
-    // Scale factor = earth radius in m / 1 AU in m.
-    const double sf = 6.37814e6 / 149.59787e9;
-
-    FILE *focd = openCP(fnOcd, ocdSpec);
-    if (!focd)
-       fatal1(msgOpen, fnOcd);
-
-    const int LINE_SIZE = 82;
-    char line[LINE_SIZE];
-    if (!fgets(line, LINE_SIZE, focd))
-       fatal1(msgRead, fnOcd);
-
-    do {
-       int idx = parseCod3(line);
-       if (idx < 0)
-          continue;
-
-       double lon,rcos,rsin;
-       errno = 0;
-       line[30] = 0;
-       rsin = mustStrtod(line+21);
-       line[21] = 0;
-       rcos = mustStrtod(line+13);
-       line[13] = 0;
-       lon = mustStrtod(line+4);
-       if (errno)
-          continue;
-
-       site *ps = siteTable+idx;
[…]

### 2022-05-16 digest2/archive/09/digest2.c

@@ -1,774 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-   {"help",    no_argument, 0, 'h'},
-   {"version", no_argument, 0, 'v'},
-   {"config",      required_argument, 0, 'c'},
-   {"model",       required_argument, 0, 'm'},
-   {"obscodes",    required_argument, 0, 'o'},
-   {"config-path", required_argument, 0, 'p'},
-   {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
[…]

### 2022-05-16 digest2/archive/09/muk.c

@@ -1,306 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
--------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <math.h>
[…]

### 2022-05-16 digest2/archive/10/d2model.c

@@ -1,247 +1,0 @@
-//! C99
-
-/* d2model.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-d2model.c
-
-defines object classes available to digest2.  (where object and class are
-not oop terms.  object=solar system object, class=orbit classification.)
-*/
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double  modelAllSS    [QX][EX][IX][HX];
-double  modelUnkSS    [QX][EX][IX][HX];
-double  modelAllClass [D2CLASSES][QX][EX][IX][HX];
-double  modelUnkClass [D2CLASSES][QX][EX][IX][HX];
-
-double  qpart[QX] = { .4 ,  .7, .8,  .9, 1. , 1.1, 1.2, 1.3, 1.4, 1.5,
-                     1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3. , 3.2, 3.5,
-                     4.  , 4.5, 5., 5.5, 10., 20., 30., 40., 100.};
-double  epart[EX] = {.1, .2, .3, .4, .5, .7, .9, 1.1};
-double  ipart[IX] = {2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180};
-double  hpart[HX] = { 6,  8, 10, 11, 12, 13, 14, 15, 16, 17,
-                     18, 19, 20, 21, 22, 23, 24, 25.5};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]) {
-   _Bool r;
-   if ((r = qeiToBin(q, e, i, bin)))
-      bin[3] = hToBin(h);
-   return r;
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3]) {
-   for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-      if (bin[0] == QX)
-         return 0;
-   for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
[…]

### 2022-05-16 digest2/archive/10/d2model.h

@@ -1,40 +1,0 @@
-//! C99
-
-/* d2model.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-// extents for model
-#define D2CLASSES 15
-#define QX 29
-#define EX 8
-#define IX 11
-#define HX 18
-
-// model
-extern double  modelAllSS    [QX][EX][IX][HX];
-extern double  modelUnkSS    [QX][EX][IX][HX];
-extern double  modelAllClass [D2CLASSES][QX][EX][IX][HX];
-extern double  modelUnkClass [D2CLASSES][QX][EX][IX][HX];
-
-// partition arrays
-extern double  qpart[QX];
-extern double  epart[EX];
-extern double  ipart[IX];
-extern double  hpart[HX];
-
-typedef _Bool (*classtest)(double, double, double, double);
-
-extern char *classAbbr[D2CLASSES];
-extern char *classHeading[D2CLASSES];
-extern classtest isClass[D2CLASSES];
-
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]);
-_Bool qeiToBin(double q, double e, double i, int bin[3]);
-int hToBin(double h);
-

### 2022-05-16 digest2/archive/10/digest2.c

@@ -1,774 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-   {"help",    no_argument, 0, 'h'},
-   {"version", no_argument, 0, 'v'},
-   {"config",      required_argument, 0, 'c'},
-   {"model",       required_argument, 0, 'm'},
-   {"obscodes",    required_argument, 0, 'o'},
-   {"config-path", required_argument, 0, 'p'},
-   {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage; // staging for tracklet to be scored
-tracklet **ring; // ring data structure
-int ringFree;    // number of free trackets
-int ringNext;    // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
[…]

### 2022-05-16 digest2/archive/10/digest2.h

@@ -1,161 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-*/
-
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-// observation.
-typedef struct {
-   double mjd;  // modified julian date
-   double ra;   // radians
-   double dec;
-   double vmag;  // observed magnitude, normalized to V band.
-                 // 0 means no magnitude.
-   int    site;  // index into site table.  basically an integer form of the
-                 // MPC three character obscode.
-   _Bool  spacebased;
-   double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants.
-typedef struct {
-   double longitude;  // unit is circles
-   double rhoCosPhi;  // unit is AU
-   double rhoSinPhi;
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-   INVALID,
-   UNPROC,
-   ACRON,
-   FAIL,
-   SUCCESS
-} tkstatus;
-
-typedef struct {
-   double rawScore;
-   double noIdScore;
-   _Bool  tagInClass[QX][EX][IX][HX];
-   _Bool  tagOutOfClass[QX][EX][IX][HX];
-   double sumAllInClass;
-   double sumUnkInClass;
-   double sumAllOutOfClass;
-   double sumUnkOutOfClass;
-   _Bool  dInClass[QX][EX][IX][HX];
-   _Bool  dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-   // these few elements really describe the tracklet
-   tkstatus status;
-   char desig[13];
-   observation *olist;
-   int obsCap; // allocated capacity of olist
-   int lines;  // for status=INVALID, this is the number of consecutive
-               // invalid lines.  otherwise, it is the number of valid
-               // observations in olist.
-
-   // distance independent working variables.  computed over the course
[…]

### 2022-05-16 digest2/archive/10/muk.c

@@ -1,310 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-
--------------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
--------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <math.h>
[…]

### 2022-05-16 digest2/archive/11/d2math.c

@@ -1,1142 +1,0 @@
-// ! C99
-
-/* d2math.c
- * 
- * Copyright (c) 2010 Sonia Keys Copyright (c) 2005,2006 Kyle Smalley,
- * Carl Hergenrother, Robert McNaught, David Asher
- * 
- * See external file LICENSE, distributed with this software.
- */
-
-/*----------------------------------------------------------------------------
- * d2math.c
- *
- * the heart of digest2. i/o, file formats, and so on are in other .c files.
- * this file contains stuff like vector math, orbit calculations, and bin
- * statistics.
- * "q" bin model is q, e, i, h, non - uniform bin spacing.
- */
-
-#include <assert.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-#include "digest2.h"
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05        // AU
-#define MAX_DISTANCE 100.       // AU
-#define minDistanceStep .2      // AU
-#define minAngleStep .1         // radian
-#define ageLimit 1
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-double obsErr;
-regex_t rxObsErr;
-
-void initGlobals(void)
-{
-    // a little bit of one time setup 
-    K = .01720209895;
-    INV_K = 1. / K;
-    U = K * K;
-    TWO_PI = M_PI * 2.;
-    arcsecrad = M_PI / (180 * 3600);
-    rtol = arcsecrad;
-
-    // Random numbers are used in aRange() in this file.  Linear
-    // congruential generator (LCG) code is here because library
-    // rand() has overhead from thread-safe stuff I don't need.
-    // I use time(0) here to get a different seed for every program run,
-    // then rand() in the per-thread setup in main() (in digest2.c)
-    // to get a different LCG seed for each thread.
-    srand(time(0));
-    LCGA = pow(13, 13);         // per NAG
-    LCGM = 1;
-    LCGM <<= 59;
-    invLCGM = 1. / LCGM;
-    LCGM--;
-    obsErr = 1 * arcsecrad;
-    assert(regcomp
[…]

### 2022-05-16 digest2/archive/11/d2model.c

@@ -1,270 +1,0 @@
-//! C99
-
-/* d2model.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-d2model.c
-
-defines object classes available to digest2.  (where object and class are
-not oop terms.  object=solar system object, class=orbit classification.)
-*/
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double modelAllSS[QX][EX][IX][HX];
-double modelUnkSS[QX][EX][IX][HX];
-double modelAllClass[D2CLASSES][QX][EX][IX][HX];
-double modelUnkClass[D2CLASSES][QX][EX][IX][HX];
-
-double qpart[QX] = { .4, .7, .8, .9, 1., 1.1, 1.2, 1.3, 1.4, 1.5,
-    1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3., 3.2, 3.5,
-    4., 4.5, 5., 5.5, 10., 20., 30., 40., 100.
-};
-double epart[EX] = { .1, .2, .3, .4, .5, .7, .9, 1.1 };
-double ipart[IX] = { 2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180 };
-double hpart[HX] = { 6, 8, 10, 11, 12, 13, 14, 15, 16, 17,
-    18, 19, 20, 21, 22, 23, 24, 25.5
-};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order
-   q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4])
-{
-    _Bool r;
-    if ((r = qeiToBin(q, e, i, bin)))
-        bin[3] = hToBin(h);
-    return r;
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3])
-{
-    for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-        if (bin[0] == QX)
-            return 0;
-    for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
-        if (bin[1] == EX)
-            return 0;
[…]

### 2022-05-16 digest2/archive/11/d2model.h

@@ -1,37 +1,0 @@
-//! C99
-
-/* d2model.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-// extents for model
-#define D2CLASSES 15
-#define QX 29
-#define EX 8
-#define IX 11
-#define HX 18
-
-// model
-extern double modelAllSS[QX][EX][IX][HX];
-extern double modelUnkSS[QX][EX][IX][HX];
-extern double modelAllClass[D2CLASSES][QX][EX][IX][HX];
-extern double modelUnkClass[D2CLASSES][QX][EX][IX][HX];
-
-// partition arrays
-extern double qpart[QX];
-extern double epart[EX];
-extern double ipart[IX];
-extern double hpart[HX];
-
-typedef _Bool(*classtest) (double, double, double, double);
-
-extern char *classAbbr[D2CLASSES];
-extern char *classHeading[D2CLASSES];
-extern classtest isClass[D2CLASSES];
-
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]);
-_Bool qeiToBin(double q, double e, double i, int bin[3]);
-int hToBin(double h);

### 2022-05-16 digest2/archive/11/d2mpc.c

@@ -1,205 +1,0 @@
-//! C99
-
-/* mpc.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <ctype.h>
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-1999 on successful parse.
-   -1 on failure.
-*/
-int parseCod3(char *cod3)
-{
-    int hp;
-
-    if (isdigit(*cod3))
-        hp = *cod3 - '0';
-    else if (*cod3 >= 'A' && *cod3 <= 'J')
-        hp = *cod3 - 'A' + 10;
-    else
-        return -1;
-
-    if (isdigit(cod3[1]) && isdigit(cod3[2]))
-        return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-    return -1;
-}
-
-/* readMpcOcd()
-
-read obscode.dat into memory.
-
-Notes:
-   On error, prints message to stdout and terminates program.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
-   Converted here to circles for easier use later.
-*/
-void readMpcOcd(void)
-{
-    site *psite = siteTable;
-    for (int i = 0; i < 1999; i++, psite++) {
-        psite->obsErr = -1;     // means unspecified
-    }
-    // Scale factor = earth radius in m / 1 AU in m.
-    const double sf = 6.37814e6 / 149.59787e9;
-
-    FILE *focd = openCP(fnOcd, ocdSpec);
-    if (!focd)
-        fatal1(msgOpen, fnOcd);
-
-    const int LINE_SIZE = 82;
-    char line[LINE_SIZE];
-    if (!fgets(line, LINE_SIZE, focd))
-        fatal1(msgRead, fnOcd);
-
-    do {
-        int idx = parseCod3(line);
-        if (idx < 0)
-            continue;
-
-        double lon, rcos, rsin;
-        errno = 0;
-        line[30] = 0;
-        rsin = mustStrtod(line + 21);
-        line[21] = 0;
-        rcos = mustStrtod(line + 13);
-        line[13] = 0;
-        lon = mustStrtod(line + 4);
-        if (errno)
[…]

### 2022-05-16 digest2/archive/11/digest2.c

@@ -1,842 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-    "Digest2 version 0.11 -- Released Jun 28 2011 -- Compiled %s\n";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-    {"help", no_argument, 0, 'h'},
-    {"version", no_argument, 0, 'v'},
-    {"config", required_argument, 0, 'c'},
-    {"model", required_argument, 0, 'm'},
-    {"obscodes", required_argument, 0, 'o'},
-    {"config-path", required_argument, 0, 'p'},
-    {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
[…]

### 2022-05-16 digest2/archive/11/digest2.h

@@ -1,169 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <regex.h>
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-
-// observation.
-typedef struct {
-    double mjd;                 // modified julian date
-    double ra;                  // radians
-    double dec;
-    double vmag;                // observed magnitude, normalized to V band.
-    // 0 means no magnitude.
-    int site;                   // index into site table.  basically an integer form of the
-    // MPC three character obscode.
-    _Bool spacebased;
-    double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants and standard observational error
-typedef struct {
-    double longitude;           // unit is circles
-    double rhoCosPhi;           // unit is AU
-    double rhoSinPhi;
-    double obsErr;              // unit is radians
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-    INVALID,
-    UNPROC,
-    ACRON,
-    FAIL,
-    SUCCESS
-} tkstatus;
-
-typedef struct {
-    double rawScore;
-    double noIdScore;
-    _Bool tagInClass[QX][EX][IX][HX];
-    _Bool tagOutOfClass[QX][EX][IX][HX];
-    double sumAllInClass;
-    double sumUnkInClass;
-    double sumAllOutOfClass;
-    double sumUnkOutOfClass;
-    _Bool dInClass[QX][EX][IX][HX];
-    _Bool dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-    // these few elements really describe the tracklet
-    tkstatus status;
-    char desig[13];
-    observation *olist;
-    int obsCap;                 // allocated capacity of olist
-    // for status=INVALID, this is the number of consecutive
-    // invalid lines.  otherwise, it is the number of valid
-    // observations in olist.
-    int lines;
-
[…]

### 2022-05-16 digest2/archive/11/muk.c

@@ -1,326 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
-------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-
-#include "d2model.h"
-
-#define LINE_SIZE 300
-
[…]

### 2022-05-16 digest2/archive/12/d2math.c

@@ -1,1164 +1,0 @@
-// ! C99
-
-/* d2math.c
- * 
- * Copyright (c) 2010 Sonia Keys Copyright (c) 2005,2006 Kyle Smalley,
- * Carl Hergenrother, Robert McNaught, David Asher
- * 
- * See external file LICENSE, distributed with this software.
- */
-
-/*----------------------------------------------------------------------------
- * d2math.c
- *
- * the heart of digest2. i/o, file formats, and so on are in other .c files.
- * this file contains stuff like vector math, orbit calculations, and bin
- * statistics.
- * "q" bin model is q, e, i, h, non - uniform bin spacing.
- */
-
-#include <assert.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-#include "digest2.h"
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05        // AU
-#define MAX_DISTANCE 100.       // AU
-#define minDistanceStep .2      // AU
-#define minAngleStep .1         // radian
-#define ageLimit 1
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-double obsErr;
-regex_t rxObsErr;
-
-void initGlobals(void)
-{
-    // a little bit of one time setup 
-    K = .01720209895;
-    INV_K = 1. / K;
-    U = K * K;
-    TWO_PI = M_PI * 2.;
-    arcsecrad = M_PI / (180 * 3600);
-    rtol = arcsecrad;
-
-    // Random numbers are used in aRange() in this file.  Linear
-    // congruential generator (LCG) code is here because library
-    // rand() has overhead from thread-safe stuff I don't need.
-    // I use time(0) here to get a different seed for every program run,
-    // then rand() in the per-thread setup in main() (in digest2.c)
-    // to get a different LCG seed for each thread.
-    srand(time(0));
-    LCGA = pow(13, 13);         // per NAG
-    LCGM = 1;
-    LCGM <<= 59;
-    invLCGM = 1. / LCGM;
-    LCGM--;
-    obsErr = 1 * arcsecrad;
-    assert(regcomp
[…]

### 2022-05-16 digest2/archive/12/digest2.c

@@ -1,848 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010-2012 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-    "Digest2 version 0.12 -- Released May 22 2012 -- Compiled %s\n";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-    {"help", no_argument, 0, 'h'},
-    {"version", no_argument, 0, 'v'},
-    {"config", required_argument, 0, 'c'},
-    {"model", required_argument, 0, 'm'},
-    {"obscodes", required_argument, 0, 'o'},
-    {"config-path", required_argument, 0, 'p'},
-    {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
[…]

### 2022-05-16 digest2/archive/12/digest2.h

@@ -1,170 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2010 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <regex.h>
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-
-// observation.
-typedef struct {
-    double mjd;                 // modified julian date
-    double ra;                  // radians
-    double dec;
-    double vmag;                // observed magnitude, normalized to V band.
-    // 0 means no magnitude.
-    int site;                   // index into site table.  basically an integer form of the
-    // MPC three character obscode.
-    _Bool spacebased;
-    double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants and standard observational error
-typedef struct {
-    double longitude;           // unit is circles
-    double rhoCosPhi;           // unit is AU
-    double rhoSinPhi;
-    double obsErr;              // unit is radians
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-    INVALID,
-    UNPROC,
-    ACRON,
-    FAIL,
-    SUCCESS
-} tkstatus;
-
-typedef struct {
-    double rawScore;
-    double noIdScore;
-    _Bool tagInClass[QX][EX][IX][HX];
-    _Bool tagOutOfClass[QX][EX][IX][HX];
-    double sumAllInClass;
-    double sumUnkInClass;
-    double sumAllOutOfClass;
-    double sumUnkOutOfClass;
-    _Bool dInClass[QX][EX][IX][HX];
-    _Bool dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-    // these few elements really describe the tracklet
-    tkstatus status;
-    char desig[13];
-    observation *olist;
-    int obsCap;                 // allocated capacity of olist
-    // for status=INVALID, this is the number of consecutive
-    // invalid lines.  otherwise, it is the number of valid
-    // observations in olist.
-    int lines;
-
[…]

### 2022-05-16 digest2/archive/13/d2math.c

@@ -1,1168 +1,0 @@
-// ! C99
-
-/* d2math.c
- * 
- * Copyright (c) 2012 Sonia Keys Copyright (c) 2005,2006 Kyle Smalley,
- * Carl Hergenrother, Robert McNaught, David Asher
- * 
- * See external file LICENSE, distributed with this software.
- */
-
-/*----------------------------------------------------------------------------
- * d2math.c
- *
- * the heart of digest2. i/o, file formats, and so on are in other .c files.
- * this file contains stuff like vector math, orbit calculations, and bin
- * statistics.
- * "q" bin model is q, e, i, h, non - uniform bin spacing.
- */
-
-#include <assert.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-#include "digest2.h"
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05        // AU
-#define MAX_DISTANCE 100.       // AU
-#define minDistanceStep .2      // AU
-#define minAngleStep .1         // radian
-#define ageLimit 1
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-double obsErr;
-regex_t rxObsErr;
-
-void initGlobals(void)
-{
-    // a little bit of one time setup 
-    K = .01720209895;
-    INV_K = 1. / K;
-    U = K * K;
-    TWO_PI = M_PI * 2.;
-    arcsecrad = M_PI / (180 * 3600);
-    rtol = arcsecrad;
-
-    // Random numbers are used in aRange() in this file.  Linear
-    // congruential generator (LCG) code is here because library
-    // rand() has overhead from thread-safe stuff I don't need.
-    // I use time(0) here to get a different seed for every program run,
-    // then rand() in the per-thread setup in main() (in digest2.c)
-    // to get a different LCG seed for each thread.
-    srand(time(0));
-    LCGA = pow(13, 13);         // per NAG
-    LCGM = 1;
-    LCGM <<= 59;
-    invLCGM = 1. / LCGM;
-    LCGM--;
-    obsErr = 1 * arcsecrad;
-    assert(regcomp
[…]

### 2022-05-16 digest2/archive/13/d2mpc.c

@@ -1,205 +1,0 @@
-//! C99
-
-/* mpc.c
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <ctype.h>
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-1999 on successful parse.
-   -1 on failure.
-*/
-int parseCod3(char *cod3)
-{
-    int hp;
-
-    if (isdigit(*cod3))
-        hp = *cod3 - '0';
-    else if (*cod3 >= 'A' && *cod3 <= 'J')
-        hp = *cod3 - 'A' + 10;
-    else
-        return -1;
-
-    if (isdigit(cod3[1]) && isdigit(cod3[2]))
-        return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-    return -1;
-}
-
-/* readMpcOcd()
-
-read obscode.dat into memory.
-
-Notes:
-   On error, prints message to stdout and terminates program.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
-   Converted here to circles for easier use later.
-*/
-void readMpcOcd(void)
-{
-    site *psite = siteTable;
-    for (int i = 0; i < 1999; i++, psite++) {
-        psite->obsErr = -1;     // means unspecified
-    }
-    // Scale factor = earth radius in m / 1 AU in m.
-    const double sf = 6.37814e6 / 149.59787e9;
-
-    FILE *focd = openCP(fnOcd, ocdSpec);
-    if (!focd)
-        fatal1(msgOpen, fnOcd);
-
-    const int LINE_SIZE = 82;
-    char line[LINE_SIZE];
-    if (!fgets(line, LINE_SIZE, focd))
-        fatal1(msgRead, fnOcd);
-
-    do {
-        int idx = parseCod3(line);
-        if (idx < 0)
-            continue;
-
-        double lon, rcos, rsin;
-        errno = 0;
-        line[30] = 0;
-        rsin = mustStrtod(line + 21);
-        line[21] = 0;
-        rcos = mustStrtod(line + 13);
-        line[13] = 0;
-        lon = mustStrtod(line + 4);
-        if (errno)
[…]

### 2022-05-16 digest2/archive/13/digest2.c

@@ -1,851 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010-2012 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-    "Digest2 version 0.13 -- Released June 8 2012 -- Compiled %s\n";
-char msgCopyright[] =
-    "(c) 2012 Sonia Keys.  See LICENSE.";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-    {"help", no_argument, 0, 'h'},
-    {"version", no_argument, 0, 'v'},
-    {"config", required_argument, 0, 'c'},
-    {"model", required_argument, 0, 'm'},
-    {"obscodes", required_argument, 0, 'o'},
-    {"config-path", required_argument, 0, 'p'},
-    {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
[…]

### 2022-05-16 digest2/archive/13/digest2.h

@@ -1,170 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <regex.h>
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-
-// observation.
-typedef struct {
-    double mjd;                 // modified julian date
-    double ra;                  // radians
-    double dec;
-    double vmag;                // observed magnitude, normalized to V band.
-    // 0 means no magnitude.
-    int site;                   // index into site table.  basically an integer form of the
-    // MPC three character obscode.
-    _Bool spacebased;
-    double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants and standard observational error
-typedef struct {
-    double longitude;           // unit is circles
-    double rhoCosPhi;           // unit is AU
-    double rhoSinPhi;
-    double obsErr;              // unit is radians
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-    INVALID,
-    UNPROC,
-    ACRON,
-    FAIL,
-    SUCCESS
-} tkstatus;
-
-typedef struct {
-    double rawScore;
-    double noIdScore;
-    _Bool tagInClass[QX][EX][IX][HX];
-    _Bool tagOutOfClass[QX][EX][IX][HX];
-    double sumAllInClass;
-    double sumUnkInClass;
-    double sumAllOutOfClass;
-    double sumUnkOutOfClass;
-    _Bool dInClass[QX][EX][IX][HX];
-    _Bool dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-    // these few elements really describe the tracklet
-    tkstatus status;
-    char desig[13];
-    observation *olist;
-    int obsCap;                 // allocated capacity of olist
-    // for status=INVALID, this is the number of consecutive
-    // invalid lines.  otherwise, it is the number of valid
-    // observations in olist.
-    int lines;
-
[…]

### 2022-05-16 digest2/archive/13/muk.c

@@ -1,326 +1,0 @@
-//! C99
-
-/* muk.c
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-muk.c
-
-This program preprocesses an asteroid model for use by Digest2.
-
-There are two inputs.  A model of the predicted entire asteroid population, and
-a list of known asteroids.  The predicted model is S3M, a list of synthetic
-orbits.  The list of known asteroids is astorb.dat.
-
-Digest2 uses the 4-D histogram format in variations that allow it
-to easily compute statistics.  The variations are:
-
-all_ss:      The input model, binned into the histogram.
-unk_ss:      A subset of the model representing only undiscovered objects.
-all_class:   A subset of the model with only orbits of a certain class, such
-             as "NEO"
-unk_class:   A subset of the model representing only undiscovered
-             objects of the class.
-
-These arrays are dumped to the file digest2.muk as program output.
-
-------------------------------------------------------------------------------
-Some notes on use of astorb.dat:
-
-The "No-ID" score of digest2 is meaningful when applied to observations which
-have failed to identify with known objects.  Thus, the meaning of "known" to
-this program is "objects which are reliably identifiable given the short arcs
-input to Digest2."  This set is not well defined, especially without knowledge
-of identification techniques used.  This program uses ephemeris uncertainty
-though, as a simple way of selecting a subset of cataloged objects that would
-likely identify.
-
-Astorb.dat was chosen because it is easy to obtain and use and because it
-provides computed ephemeris uncertainties.  Of the various uncertainties
-provided.  This program uses Parameter 24, which is a peak uncertainty over a
-period of at least ten years, and it selects asteroids with an uncertainty of 1
-arc minute or less.
-*/
-
-#include <errno.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-
-#include "d2model.h"
-
-#define LINE_SIZE 300
-
[…]

### 2022-05-16 digest2/archive/14/digest2.c

@@ -1,862 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010-2013 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-    "Digest2 version 0.14 -- Released January 10 2013 -- Compiled %s\n";
-char msgCopyright[] =
-    "(c) 2013 Sonia Keys.  See LICENSE.";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-    {"help", no_argument, 0, 'h'},
-    {"version", no_argument, 0, 'v'},
-    {"config", required_argument, 0, 'c'},
-    {"model", required_argument, 0, 'm'},
-    {"obscodes", required_argument, 0, 'o'},
-    {"config-path", required_argument, 0, 'p'},
-    {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
[…]

### 2022-05-16 digest2/archive/15/digest2.c

@@ -1,862 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010-2013 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-    "Digest2 version 0.15 -- Released February 20 2013 -- Compiled %s\n";
-char msgCopyright[] =
-    "(c) 2013 Sonia Keys.  See LICENSE.";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:";
-struct option lOpt[] = {
-    {"help", no_argument, 0, 'h'},
-    {"version", no_argument, 0, 'v'},
-    {"config", required_argument, 0, 'c'},
-    {"model", required_argument, 0, 'm'},
-    {"obscodes", required_argument, 0, 'o'},
-    {"config-path", required_argument, 0, 'p'},
-    {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
[…]

### 2022-05-16 digest2/archive/15/digest2.h

@@ -1,171 +1,0 @@
-/*
-digest2.h
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <regex.h>
-#include <stdint.h>
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-
-// observation.
-typedef struct {
-    double mjd;                 // modified julian date
-    double ra;                  // radians
-    double dec;
-    double vmag;                // observed magnitude, normalized to V band.
-    // 0 means no magnitude.
-    int site;                   // index into site table.  basically an integer form of the
-    // MPC three character obscode.
-    _Bool spacebased;
-    double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants and standard observational error
-typedef struct {
-    double longitude;           // unit is circles
-    double rhoCosPhi;           // unit is AU
-    double rhoSinPhi;
-    double obsErr;              // unit is radians
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-    INVALID,
-    UNPROC,
-    ACRON,
-    FAIL,
-    SUCCESS
-} tkstatus;
-
-typedef struct {
-    double rawScore;
-    double noIdScore;
-    _Bool tagInClass[QX][EX][IX][HX];
-    _Bool tagOutOfClass[QX][EX][IX][HX];
-    double sumAllInClass;
-    double sumUnkInClass;
-    double sumAllOutOfClass;
-    double sumUnkOutOfClass;
-    _Bool dInClass[QX][EX][IX][HX];
-    _Bool dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-    // these few elements really describe the tracklet
-    tkstatus status;
-    char desig[13];
-    observation *olist;
-    int obsCap;                 // allocated capacity of olist
-    // for status=INVALID, this is the number of consecutive
-    // invalid lines.  otherwise, it is the number of valid
-    // observations in olist.
-    int lines;
-
[…]

### 2022-05-16 digest2/archive/16/d2math.c

@@ -1,1171 +1,0 @@
-// ! C99
-
-/* d2math.c
- * 
- * Copyright (c) 2012 Sonia Keys Copyright (c) 2005,2006 Kyle Smalley,
- * Carl Hergenrother, Robert McNaught, David Asher
- * 
- * See external file LICENSE, distributed with this software.
- */
-
-/*----------------------------------------------------------------------------
- * d2math.c
- *
- * the heart of digest2. i/o, file formats, and so on are in other .c files.
- * this file contains stuff like vector math, orbit calculations, and bin
- * statistics.
- * "q" bin model is q, e, i, h, non - uniform bin spacing.
- */
-
-#include <assert.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-#include "digest2.h"
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05        // AU
-#define MAX_DISTANCE 100.       // AU
-#define minDistanceStep .2      // AU
-#define minAngleStep .1         // radian
-#define ageLimit 1
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-double obsErr;
-regex_t rxObsErr;
-
-void initGlobals(void)
-{
-    // a little bit of one time setup 
-    K = .01720209895;
-    INV_K = 1. / K;
-    U = K * K;
-    TWO_PI = M_PI * 2.;
-    arcsecrad = M_PI / (180 * 3600);
-    rtol = arcsecrad;
-
-    // Random numbers are used in aRange() in this file.  Linear
-    // congruential generator (LCG) code is here because library
-    // rand() has overhead from thread-safe stuff I don't need.
-    // I use time(0) here to get a different seed for every program run,
-    // then rand() in the per-thread setup in main() (in digest2.c)
-    // to get a different LCG seed for each thread.
-    srand(time(0));
-    LCGA = pow(13, 13);         // per NAG
-    LCGM = 1;
-    LCGM <<= 59;
-    invLCGM = 1. / LCGM;
-    LCGM--;
-    obsErr = 1 * arcsecrad;
-    assert(regcomp
[…]

### 2022-05-16 digest2/archive/16/d2model.c

@@ -1,270 +1,0 @@
-//! C99
-
-/* d2model.c
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-d2model.c
-
-defines object classes available to digest2.  (where object and class are
-not oop terms.  object=solar system object, class=orbit classification.)
-*/
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double modelAllSS[QX][EX][IX][HX];
-double modelUnkSS[QX][EX][IX][HX];
-double modelAllClass[D2CLASSES][QX][EX][IX][HX];
-double modelUnkClass[D2CLASSES][QX][EX][IX][HX];
-
-double qpart[QX] = { .4, .7, .8, .9, 1., 1.1, 1.2, 1.3, 1.4, 1.5,
-    1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3., 3.2, 3.5,
-    4., 4.5, 5., 5.5, 10., 20., 30., 40., 100.
-};
-double epart[EX] = { .1, .2, .3, .4, .5, .7, .9, 1.1 };
-double ipart[IX] = { 2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180 };
-double hpart[HX] = { 6, 8, 10, 11, 12, 13, 14, 15, 16, 17,
-    18, 19, 20, 21, 22, 23, 24, 25.5
-};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order
-   q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4])
-{
-    _Bool r;
-    if ((r = qeiToBin(q, e, i, bin)))
-        bin[3] = hToBin(h);
-    return r;
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3])
-{
-    for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-        if (bin[0] == QX)
-            return 0;
-    for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
-        if (bin[1] == EX)
-            return 0;
[…]

### 2022-05-16 digest2/archive/16/d2model.h

@@ -1,37 +1,0 @@
-//! C99
-
-/* d2model.h
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-// extents for model
-#define D2CLASSES 15
-#define QX 29
-#define EX 8
-#define IX 11
-#define HX 18
-
-// model
-extern double modelAllSS[QX][EX][IX][HX];
-extern double modelUnkSS[QX][EX][IX][HX];
-extern double modelAllClass[D2CLASSES][QX][EX][IX][HX];
-extern double modelUnkClass[D2CLASSES][QX][EX][IX][HX];
-
-// partition arrays
-extern double qpart[QX];
-extern double epart[EX];
-extern double ipart[IX];
-extern double hpart[HX];
-
-typedef _Bool(*classtest) (double, double, double, double);
-
-extern char *classAbbr[D2CLASSES];
-extern char *classHeading[D2CLASSES];
-extern classtest isClass[D2CLASSES];
-
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]);
-_Bool qeiToBin(double q, double e, double i, int bin[3]);
-int hToBin(double h);

### 2022-05-16 digest2/archive/16/d2mpc.c

@@ -1,205 +1,0 @@
-//! C99
-
-/* mpc.c
-
-Copyright (c) 2012 Sonia Keys
-
-See external file LICENSE, distributed with this software.
-*/
-
-#include <ctype.h>
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-3599 on successful parse. (3599 = obscodeNamespaceSize - 1)
-   -1 on failure.
-*/
-int parseCod3(char *cod3)
-{
-    int hp;
-
-    if (isdigit(*cod3))
-        hp = *cod3 - '0';
-    else if (*cod3 >= 'A' && *cod3 <= 'Z')
-        hp = *cod3 - 'A' + 10;
-    else
-        return -1;
-
-    if (isdigit(cod3[1]) && isdigit(cod3[2]))
-        return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-    return -1;
-}
-
-/* readMpcOcd()
-
-read obscode.dat into memory.
-
-Notes:
-   On error, prints message to stdout and terminates program.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
-   Converted here to circles for easier use later.
-*/
-void readMpcOcd(void)
-{
-    site *psite = siteTable;
-    for (int i = 0; i < obscodeNamespaceSize; i++, psite++) {
-        psite->obsErr = -1;     // means unspecified
-    }
-    // Scale factor = earth radius in m / 1 AU in m.
-    const double sf = 6.37814e6 / 149.59787e9;
-
-    FILE *focd = openCP(fnOcd, ocdSpec);
-    if (!focd)
-        fatal1(msgOpen, fnOcd);
-
-    const int LINE_SIZE = 82;
-    char line[LINE_SIZE];
-    if (!fgets(line, LINE_SIZE, focd))
-        fatal1(msgRead, fnOcd);
-
-    do {
-        int idx = parseCod3(line);
-        if (idx < 0)
-            continue;
-
-        double lon, rcos, rsin;
-        errno = 0;
-        line[30] = 0;
-        rsin = mustStrtod(line + 21);
-        line[21] = 0;
-        rcos = mustStrtod(line + 13);
-        line[13] = 0;
[…]

### 2022-05-16 digest2/archive/16/digest2.c

@@ -1,872 +1,0 @@
-//! C99
-
-/* Digest2.c
-
-Copyright (c) 2010-2013 Sonia Keys
-Copyright (c) 2005,2006 Kyle Smalley, Carl Hergenrother, Robert McNaught,
-David Asher
-
-See external file LICENSE, distributed with this software.
-*/
-
-/*-----------------------------------------------------------------------------
-Digest2.c
-
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-#include <ctype.h>
-#include <errno.h>
-#include <getopt.h>
-#include <limits.h>
-#include <math.h>
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-    "Digest2 version 0.16 -- Released February 20 2015 -- Compiled %s\n";
-char msgCopyright[] =
-    "(c) 2013 Sonia Keys.  See LICENSE.";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char sOpt[] = "hvc:m:o:p:u:";
-struct option lOpt[] = {
-    {"help", no_argument, 0, 'h'},
-    {"version", no_argument, 0, 'v'},
-    {"config", required_argument, 0, 'c'},
-    {"model", required_argument, 0, 'm'},
-    {"obscodes", required_argument, 0, 'o'},
-    {"config-path", required_argument, 0, 'p'},
-    {"cpu", required_argument, 0, 'u'},
-    {0, 0, 0, 0}
-};
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-_Bool cpuSpec = 0;
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
[…]

### 2022-05-16 digest2/archive/16/s3mbin.c

@@ -1,172 +1,0 @@
-//! C99
-
-// s3mbin.c
-
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-
-#include "d2model.h"
-
-#define LINE_SIZE 300
-
-// structure of binned population model
-
-double all_ss[QX][EX][IX][HX];
-double all_class[D2CLASSES][QX][EX][IX][HX];
-
-int nAll, nOrbits;
-int nClass[D2CLASSES];
-
-void binS3m(char *fn, _Bool clipNeo)
-{
-    puts(fn);
-    char line[LINE_SIZE];
-    if (snprintf(line, LINE_SIZE, "../../s3m/%s", fn) >= LINE_SIZE) {
-        puts("Path buffer overflow");
-        exit(-1);
-    }
-    char *qfn = malloc(strlen(line) + 1);
-    if (!qfn) {
-        puts("Memory allocation failed");
-        exit(-1);
-    }
-    strcpy(qfn, line);
-    FILE *fmodel = fopen(qfn, "r");
-    if (!fmodel) {
-        printf("Open %s failed.\n", qfn);
-        exit(-1);
-    }
-
-    do
-        if (!fgets(line, LINE_SIZE, fmodel)) {
-            printf("Read %s failed.\n", qfn);
-            fclose(fmodel);
-            exit(-1);
-        }
-    while (line[0] == '!' && line[1] == '!');
-
-    int hEnd = -1;
-    sscanf(line, "%*s %*s %*f %*f %*f %*f %*f %*f %*f%n", &hEnd);
-    if (hEnd == -1) {
-        puts("Unexpected format:");
-        puts(line);
-        fclose(fmodel);
-        exit(-1);
-    }
-
-    double q, e, i, h;
-    do {
-        if (sscanf(line, "%*s %*s %lf %lf %lf %*f %*f %*f %lf",
-                   &q, &e, &i, &h) != 4 ||
-            q <= 0. || e < 0. || e > 1.1 || i < 0. || i >= 180.) {
-//         printf("Unexpected q e i h: %s\n", line);
-            continue;
-        }
-        nOrbits++;
-
-        if (clipNeo && q < 1.3) {
-//         printf("Unexpected NEO orbit: %s\n", line+qStart);
-            continue;
-        }
-
-        int bin[4];
-        if (!qeihToBin(q, e, i, h, bin))
[…]

### 2022-05-16 digest2/archive/16/s3mtest.c

@@ -1,195 +1,0 @@
-//! C99
-
-// s3mtest.c
-
-#include <errno.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-
-#include "d2model.h"
-
-#define LINE_SIZE 300
-
-_Bool isTrojan(double q, double e, double i);
-// structure of binned population model
-
-int s3m[D2CLASSES][HX];
-int aod[D2CLASSES][HX];
-
-void binS3m(char *fn, _Bool clipNeo)
-{
-    puts(fn);
-    FILE *fmodel = fopen(fn, "r");
-    if (!fmodel) {
-        printf("Open %s failed.\n", fn);
-        exit(-1);
-    }
-
-    char line[LINE_SIZE];
-    do
-        if (!fgets(line, LINE_SIZE, fmodel)) {
-            printf("Read %s failed.\n", fn);
-            fclose(fmodel);
-            exit(-1);
-        }
-    while (line[0] == '!' && line[1] == '!');
-
-    int hEnd = -1;
-    sscanf(line, "%*s %*s %*f %*f %*f %*f %*f %*f %*f%n", &hEnd);
-    if (hEnd == -1) {
-        puts("Unexpected format:");
-        puts(line);
-        fclose(fmodel);
-        exit(-1);
-    }
-
-    double q, e, i, h;
-    do {
-        if (sscanf(line, "%*s %*s %lf %lf %lf %*f %*f %*f %lf",
-                   &q, &e, &i, &h) != 4 ||
-            q <= 0. || e < 0. || e > 1. || i < 0. || i >= 180.) {
-//         printf("Unexpected q e i h: %s\n", line);
-            continue;
-        }
-
-        if (clipNeo && q < 1.3) {
-//         printf("Unexpected NEO orbit: %s\n", line);
-            continue;
-        }
-
-        if (q < 1.3 && h < 6) {
-            printf("%f %f\n", q, h);
-            puts(line);
-            exit(-1);
-        }
-        int bin[4];
-        if (!qeihToBin(q, e, i, h, bin))
-            continue;
-
-        int ih = bin[3];
-
-        for (int c = 0; c < D2CLASSES; c++)
-            if ((*isClass[c]) (q, e, i, h)) {
-                s3m[c][ih]++;
-            }
-    }
-    while (fgets(line, LINE_SIZE, fmodel));
-
-    fclose(fmodel);
-}
-
-int main()
-{
-    binS3m("../../s3m/S0.s3m", 0);      // NEO
[…]

### 2022-05-16 digest2/d2cli.c

@@ -1,419 +1,0 @@
-// d2cli.c
-//
-// Public domain.
-
-#include <assert.h>
-#include <errno.h>
-#include <getopt.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-char msgVersion[] =
-  "Digest2 version 0.19 -- Released August 16, 2017 -- Compiled %s\n";
-char msgCopyright[] = "Public domain.";
-
-// stuff used for parsing command line
-//-----------------------------------------------------------------------------
-char line[LINE_SIZE];
-char field[FIELD_SIZE];
-char sOpt[] = "hvc:m:o:p:u:l:";
-struct option lOpt[] = {
-  {"help", no_argument, 0, 'h'},
-  {"version", no_argument, 0, 'v'},
-  {"config", required_argument, 0, 'c'},
-  {"model", required_argument, 0, 'm'},
-  {"obscodes", required_argument, 0, 'o'},
-  {"config-path", required_argument, 0, 'p'},
-  {"cpu", required_argument, 0, 'u'},
-  {"limit", required_argument, 0, 'l'},
-  {0, 0, 0, 0}
-};
-
-_Bool configSpec = 0;
-_Bool modelSpec = 0;
-_Bool ocdSpec = 0;
-_Bool pathSpec = 0;
-_Bool cpuSpec = 0;
-_Bool limitSpec = 0;
-_Bool classPossible;
-_Bool raw, noid;
-_Bool headings, rms, repeatable;
-int nClassCompute;
-int nClassColumns;
-int classCompute[D2CLASSES];
-int classColumn[D2CLASSES];
-int limitClass;
-_Bool limitRaw;
-int limit;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-char *fnConfig = "digest2.config";
-char *fnModel = "digest2.model";
-char *fnCSV = "digest2.model.csv";
-char *fnOCD = "digest2.obscodes";
-char *fpConfig = "";
-
-char msgAccess[] = "Cannot access URL %s\n";
-char msgCSVHeader[] = "Invalid CSV header:  %s\n";
-char msgCSVData[] = "Invalid CSV data:  %s\n";
-char msgCSVStat[] = "%s:         %d bytes %s"; // file name, size, date
-char msgConfig[] = "Unrecognized line in config file:  %s\n";
[…]

### 2022-05-16 digest2/d2math.c

@@ -1,1143 +1,0 @@
-// d2math.c
-//
-// Public domain.
-
-/*
- * the heart of digest2. i/o, file formats, and so on are in other .c files.
- * this file contains stuff like vector math, orbit calculations, and bin
- * statistics.
- * "q" bin model is q, e, i, h, non-uniform bin spacing.
- */
-
-#include <assert.h>
-#include <math.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-#include "digest2.h"
-// near distance limit of .05 is kind of arbitrary, but seems to work.
-#define MIN_DISTANCE .05        // AU
-#define MAX_DISTANCE 100.       // AU
-#define minDistanceStep .2      // AU
-#define minAngleStep .1         // radian
-#define ageLimit 1
-double K, INV_K, U, TWO_PI;
-uint64_t LCGA, LCGM;
-double invLCGM;
-double arcsecrad, rtol;
-double obsErr;
-regex_t rxObsErr;
-
-void initGlobals(void)
-{
-  // a little bit of one time setup 
-  K = .01720209895;
-  INV_K = 1. / K;
-  U = K * K;
-  TWO_PI = M_PI * 2.;
-  arcsecrad = M_PI / (180 * 3600);
-  rtol = arcsecrad;
-
-  // Random numbers are used in aRange() in this file.  Linear
-  // congruential generator (LCG) code is here because library
-  // rand() has overhead from thread-safe stuff I don't need.
-  // I use time(0) here to get a different seed for every program run,
-  // then rand() in the per-thread setup in main() (in digest2.c)
-  // to get a different LCG seed for each thread.
-  srand(time(0));
-  LCGA = pow(13, 13);           // per NAG
-  LCGM = 1;
-  LCGM <<= 59;
-  invLCGM = 1. / LCGM;
-  LCGM--;
-  obsErr = 1 * arcsecrad;
-  assert(regcomp
-         (&rxObsErr, "^[ \t]*([^ \t=]*)[ \t]*=[ \t]*(.+)$", REG_EXTENDED) == 0);
-}
-
-/*
- * se2000
- * 
- * solar ephemeris, J2000
- * 
- * Args: mjd
- * 
- * Returns:
- * psun_earth: sun-earth vector in equatorial coordinates.
[…]

### 2022-05-16 digest2/d2model.c

@@ -1,261 +1,0 @@
-// d2model.c
-//
-// Public domain.
-
-// object classes available to digest2.  (where object and class are
-// not oop terms.  object=solar system object, class=orbit classification.)
-
-#include <math.h>
-#include "d2model.h"
-
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-double modelAllSS[QX][EX][IX][HX];
-double modelUnkSS[QX][EX][IX][HX];
-double modelAllClass[D2CLASSES][QX][EX][IX][HX];
-double modelUnkClass[D2CLASSES][QX][EX][IX][HX];
-
-double qpart[QX] = { .4, .7, .8, .9, 1., 1.1, 1.2, 1.3, 1.4, 1.5,
-  1.67, 1.8, 2., 2.2, 2.4, 2.6, 2.8, 3., 3.2, 3.5,
-  4., 4.5, 5., 5.5, 10., 20., 30., 40., 100.
-};
-double epart[EX] = { .1, .2, .3, .4, .5, .7, .9, 1.1 };
-double ipart[IX] = { 2, 5, 10, 15, 20, 25, 30, 40, 60, 90, 180 };
-
-double hpart[HX] = { 6, 8, 10, 11, 12, 13, 14, 15, 16, 17,
-  18, 19, 20, 21, 22, 23, 24, 25.5
-};
-
-/* qeihToBin
-
-convert elements q, e, i, h to bin indexes
-
-Returns:
-   true if in model, bin indexes returned in parameter 'bin' in order
-   q, e, i, h.
-   false if out of model
-*/
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4])
-{
-  _Bool r;
-  if ((r = qeiToBin(q, e, i, bin)))
-    bin[3] = hToBin(h);
-  return r;
-}
-
-_Bool qeiToBin(double q, double e, double i, int bin[3])
-{
-  for (bin[0] = 0; q >= qpart[bin[0]]; ++bin[0])
-    if (bin[0] == QX)
-      return 0;
-  for (bin[1] = 0; e >= epart[bin[1]]; ++bin[1])
-    if (bin[1] == EX)
-      return 0;
-  for (bin[2] = 0; i >= ipart[bin[2]]; ++bin[2])
-    if (bin[2] == IX)
-      return 0;
-  return 1;
-}
-
-int hToBin(double h)
-{
-  int ih;
[…]

### 2022-05-16 digest2/d2model.h

@@ -1,32 +1,0 @@
-// d2model.h
-//
-// Public domain.
-
-// extents for model
-#define D2CLASSES 15
-#define QX 29
-#define EX 8
-#define IX 11
-#define HX 18
-
-// model
-extern double modelAllSS[QX][EX][IX][HX];
-extern double modelUnkSS[QX][EX][IX][HX];
-extern double modelAllClass[D2CLASSES][QX][EX][IX][HX];
-extern double modelUnkClass[D2CLASSES][QX][EX][IX][HX];
-
-// partition arrays
-extern double qpart[QX];
-extern double epart[EX];
-extern double ipart[IX];
-extern double hpart[HX];
-
-typedef _Bool(*classtest) (double, double, double, double);
-
-extern char *classAbbr[D2CLASSES];
-extern char *classHeading[D2CLASSES];
-extern classtest isClass[D2CLASSES];
-
-_Bool qeihToBin(double q, double e, double i, double h, int bin[4]);
-_Bool qeiToBin(double q, double e, double i, int bin[3]);
-int hToBin(double h);

### 2022-05-16 digest2/d2modelio.c

@@ -1,246 +1,0 @@
-// d2modelio.c
-//
-// Public domain.
-
-// posix source added for fileno()
-#define _POSIX_SOURCE
-
-#include <math.h>
-#include <stdbool.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <time.h>
-
-#include "digest2.h"
-
-_Bool csvError(char *mod, char *class, int iq, int ie, int ii, char *heading)
-{
-  // printf("CSV error %s %s\n", mod, class);
-  // printf("Q e i = %g %g %g\n", qpart[iq], epart[ie], ipart[ii]);
-  // printf("%s field: \"%s\"\n", heading, field);
-  sprintf(line, msgCSVData, fnCSV);
-  return false;
-}
-
-// scans to ',' or end of string, copying to field as long as it fits.
-// returns pointer to character of start that terminated the scan, ',' or
-// the terminating null.  in the case where data would overflow field,
-// nothing is copied and start is returned.
-char *scanField(char *start)
-{
-  char *end = strchr(start, ',');
-  if (!end) {
-    end = strchr(start, 0);
-  }
-  int n = end - start;
-  if (n > sizeof(field) - 1) {
-    *field = 0;
-    return start;
-  }
-  memcpy(field, start, n);
-  field[n] = 0;
-  return end;
-}
-
-_Bool
-readCSVClass(FILE * fcsv, double pop[QX][EX][IX][HX], char *mod, char *class)
-{
-  char *t;
-  double d;
-  for (int iq = 0; iq < QX; iq++)
-    for (int ie = 0; ie < EX; ie++)
-      for (int ii = 0; ii < IX; ii++) {
-        fgets(line, sizeof(line), fcsv);
-        char *p = scanField(line);
-        if (*p != ',' || strcmp(field, mod) != 0) {
-          return csvError(mod, class, iq, ie, ii, "Model");
-        }
-        p = scanField(p + 1);
-        if (*p != ',' || strcmp(field, class) != 0) {
-          return csvError(mod, class, iq, ie, ii, "Class");
-        }
-        p = scanField(p + 1);
-        if (*p != ',' || fabs(strtod(field, &t) - qpart[iq]) > 1e-9) {
-          return csvError(mod, class, iq, ie, ii, "Q");
-        }
-        p = scanField(p + 1);
[…]

### 2022-05-16 digest2/d2mpc.c

@@ -1,333 +1,0 @@
-// d2mpc.c
-//
-//
-// Update Oct. 7, 2021: added band conversion 'u' and CMOS 'B', by Peter Veres
-// Public domain.
-
-#include <ctype.h>
-#include <errno.h>
-#include <limits.h>
-#include <stdio.h>
-#include <stdbool.h>
-#include <stdlib.h>
-
-#include "digest2.h"
-
-#define OCD_URL "http://www.minorplanetcenter.net/iau/lists/ObsCodes.html"
-
-// functions
-//-----------------------------------------------------------------------------
-
-/* parseCod3
-
-convert 3 character MPC obscode to integer
-
-Returns:
-   0-3599 on successful parse. (3599 = obscodeNamespaceSize - 1)
-   -1 on failure.
-*/
-int parseCod3(char *cod3)
-{
-  int hp;
-
-  if (isdigit(*cod3))
-    hp = *cod3 - '0';
-  else if (*cod3 >= 'A' && *cod3 <= 'Z')
-    hp = *cod3 - 'A' + 10;
-  else
-    return -1;
-
-  if (isdigit(cod3[1]) && isdigit(cod3[2]))
-    return hp * 100 + (cod3[1] - '0') * 10 + cod3[2] - '0';
-
-  return -1;
-}
-
-/* mustStrtod
-
-for required fields.  a version of atof that sets errno on blank input.
-also allows whitespace after sign
-*/
-double mustStrtod(char *str)
-{
-  char *endp;
-  _Bool neg = *str == '-';
-  if (neg || *str == '+')
-    str++;
-  double result = strtod(str, &endp);
-  if (!errno && endp == str)
-    errno = EINVAL;
-  return neg ? -result : result;
-}
-
-/* mustStrtoi
-
-returns int but actually disallows negatives.
-*/
-int mustStrtoi(char *str)
-{
-  char *endp;
-  long result = strtol(str, &endp, 10);
-  if (!errno)
-    if (endp == str || result < 0 || result > INT_MAX)
-      errno = EINVAL;
-  return result;
-}
-
-/* readOCD()
-
-read obscode.dat into memory.
-
-Notes:
-   On file error, leaves error message in line and returns false.
-
-   Units of rho sin/cos phi in obscode.dat are equatorial radii
-   of the Earth.  Converted to AU here for easier use later.
-   Units of longitude are degrees, 
[…]

### 2022-05-16 digest2/digest2.c

@@ -1,553 +1,0 @@
-// digest2.c
-//
-// Public domain.
-
-/*
-This program uses statistical ranging techniques on short arc astrometry to
-compute probabilities that observed objects are of various orbit classes.
-
-See external file README for additional information.
-*/
-
-#include <pthread.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <unistd.h>
-
-#include "digest2.h"
-
-// thread coordination
-//-----------------------------------------------------------------------------
-
-int cores;
-tracklet *stage;                // staging for tracklet to be scored
-tracklet **ring;                // ring data structure
-int ringFree;                   // number of free trackets
-int ringNext;                   // index of next free tracklet
-
-// deadlock avoidance:
-// a thread holding one never asks for the other.
-pthread_mutex_t mStage = PTHREAD_MUTEX_INITIALIZER;
-pthread_mutex_t mRing = PTHREAD_MUTEX_INITIALIZER;
-
-// signaled by main thread when data is staged.
-// mutex: mStage
-// pre-condition:  stage == 0
-// while locked:  set stage
-// post-condition:  stage non-zero
-pthread_cond_t cReady = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it begins work.
-// mutex: mStage
-// pre-condition:  stage non-zero
-// while locked:  zero stage
-// post-condition:  stage == 0
-pthread_cond_t cFree = PTHREAD_COND_INITIALIZER;
-
-// signaled by scoring thread when it returns a token to the ring
-// mutex: mRing
-// post-condition: ringFree > 0
-pthread_cond_t cDone = PTHREAD_COND_INITIALIZER;
-
-// "constant" global data
-//-----------------------------------------------------------------------------
-// global data that is constant, at least after being initialized, and so
-// can be shared by threads.
-
-site siteTable[obscodeNamespaceSize];
-int outputLineSize;
-char *outputLine;
-
-/* resetInvalid
-
-reset tracklet struct for processing a new object.
-
-Notes;
-   zero the struct, except retain the allocated olist and it's capacity.
-   also initialize number lines to 1.  that's all that's needed to indicate
-   an invalid observation line.
-*/
-tracklet *resetInvalid(void)
[…]

### 2022-05-16 digest2/digest2.h

@@ -1,209 +1,0 @@
-// digest2.h
-//
-// Public domain.
-
-#include <regex.h>
-#include <stdint.h>
-#include <sys/stat.h>
-
-#include "d2model.h"
-
-// M_PI is in math.h, but not defined in some strict modes
-#ifndef M_PI
-#define M_PI 3.14159265358979323846264338327
-#endif
-
-// typedefs
-//-----------------------------------------------------------------------------
-
-// observation.
-typedef struct {
-  double mjd;                   // modified julian date
-  double ra;                    // radians
-  double dec;
-  double vmag;                  // observed magnitude, normalized to V band.
-  // 0 means no magnitude.
-  int site;                     // index into site table.  basically an integer form of the
-  // MPC three character obscode.
-  _Bool spacebased;
-  double earth_observer[3];
-} observation;
-
-// site.  observatory site parallax constants and standard observational error
-typedef struct {
-  double longitude;             // unit is circles
-  double rhoCosPhi;             // unit is AU
-  double rhoSinPhi;
-  double obsErr;                // unit is radians
-} site;
-
-// tkstatus.  traklet status, during processing and as a result code.
-typedef enum {
-  INVALID,
-  UNPROC,
-  ACRON,
-  FAIL,
-  SUCCESS
-} tkstatus;
-
-typedef struct {
-  double rawScore;
-  double noIdScore;
-  _Bool tagInClass[QX][EX][IX][HX];
-  _Bool tagOutOfClass[QX][EX][IX][HX];
-  double sumAllInClass;
-  double sumUnkInClass;
-  double sumAllOutOfClass;
-  double sumUnkOutOfClass;
-  _Bool dInClass[QX][EX][IX][HX];
-  _Bool dOutOfClass[QX][EX][IX][HX];
-} perClass;
-
-// tracklet.  struct holds working variables and everything associated with
-// computing scores for a single tracklet.
-//
-// note: some code relies on this structure being zero initialized.
-typedef struct {
-  // these few elements really describe the tracklet
-  tkstatus status;
-  char desig[13];
-  observation *olist;
-  int obsCap;                   // allocated capacity of olist
-  // for status=INVALID, this is the number of consecutive
-  // invalid lines.  otherwise, it is the number of valid
-  // observations in olist.
-  int lines;
-
[…]

### 2022-05-16 neocp/neo/convert.sh
rename notebooks, consolidate

@@ -1,0 +1,6 @@
+for i in $(seq 0 199)
+do
+   printf -v two "%02d" $i
+   printf -v three "%03d" $i
+   mv night_${two}.filtered.dat night_${three}.filtered.dat
+done

### 2022-08-26 lsst_detection_probability/detection_probability.py
move code for #10 into functions

@@ -1,0 +1,169 @@
+import astropy.units as u
+from astropy.time import Time
+from astropy.coordinates import SkyCoord
+import pandas as pd
+import numpy as np
+
+from variant_orbits import variant_orbit_ephemerides
+from scheduling import get_LSST_schedule
+
+import sys
+sys.path.append("../neocp")
+from lsst_neocp import find_first_file
+
+
+def filter_tracklets(df, min_obs=2, min_arc=1, max_time=90):
+    init = SkyCoord(ra=df["RA_deg"].iloc[0], dec=df["Dec_deg"].iloc[0], unit="deg")
+    final = SkyCoord(ra=df["RA_deg"].iloc[-1], dec=df["Dec_deg"].iloc[-1], unit="deg")
+
+    return np.logical_and.reduce((len(df) >= min_obs,
+                                  init.separation(final).to(u.arcsecond).value > min_arc,
+                                  df["mjd_utc"].diff().min() * 1440 < max_time))
+
+
+def get_detection_probabilities(night_start, path="../neocp/neo/", detection_window=15, min_nights=3):
+    # create a list of nights in the detection window and get schedule for them
+    night_list = list(range(night_start, night_start + detection_window))
+    schedule = get_LSST_schedule(night=(night_start, night_start + detection_window - 1))
+
+    # offset the schedule by one row and re-merge to get the previous night column
+    shifted = schedule.shift()
+    shifted = shifted.drop("observationStartMJD", axis=1)
+    shifted = shifted.rename(columns={"fieldRA": "previousFieldRA", "fieldDec": "previousFieldDec", "night": "previousNight"})
+    full_schedule = pd.merge(schedule, shifted, left_index=True, right_index=True)
+
+    # calculate the length of each night in days
+    night_lengths = np.zeros(detection_window)
+    for i, night in enumerate(night_list):
+        mask = full_schedule["night"] == night
+        
+        # ignore nights that have no observations (bad weather/downtime)
+        if not full_schedule[mask].empty:
+            night_lengths[i] = full_schedule[mask].iloc[-1]["observationStartMJD"] - full_schedule[mask].iloc[0]["observationStartMJD"]
+
+    # get the first visit from each night
+    first_visit_each_night = full_schedule[full_schedule["night"] != full_schedule["previousNight"]]
+
+    file = find_first_file(night_list)
+    visit_file = pd.read_hdf(path + f"filtered_visit_{file:03d}.h5")
+
[…]

### 2022-08-26 lsst_detection_probability/detection_probability.py
add comments and lint detection_probability

@@ -22,6 +22,26 @@ def filter_tracklets(df, min_obs=2, min_arc=1, max_time=90):
 
 
 def get_detection_probabilities(night_start, path="../neocp/neo/", detection_window=15, min_nights=3):
+    """Get the probability that LSST will detect each object that was observed in a particular night
+
+    Parameters
+    ----------
+    night_start : `int`
+        Night of the initial observations
+    path : `str`, optional
+        Path the observation file, by default "../neocp/neo/"
+    detection_window : `int`, optional
+        How many days in the detection window, by default 15
+    min_nights : `int`, optional
+        Minimum number of nights on which observations need to have occurred, by default 3
+
+    Returns
+    -------
+    probs : `list`
+        Estimated probability that each object will be detected by LSST alone
+    will_be_detected : `list`
+        Truth of whether each object will be detected by LSST alone
+    """
     # create a list of nights in the detection window and get schedule for them
     night_list = list(range(night_start, night_start + detection_window))
     schedule = get_LSST_schedule(night=(night_start, night_start + detection_window - 1))
@@ -29,20 +49,23 @@ def get_detection_probabilities(night_start, path="../neocp/neo/", detection_win
     # offset the schedule by one row and re-merge to get the previous night column
     shifted = schedule.shift()
     shifted = shifted.drop("observationStartMJD", axis=1)
-    shifted = shifted.rename(columns={"fieldRA": "previousFieldRA", "fieldDec": "previousFieldDec", "night": "previousNight"})
+    shifted = shifted.rename(columns={"fieldRA": "previousFieldRA", "fieldDec": "previousFieldDec",
+                                      "night": "previousNight"})
     full_schedule = pd.merge(schedule, shifted, left_index=True, right_index=True)
 
     # calculate the length of each night in days
     night_lengths = np.zeros(detection_window)
     for i, night in enumerate(night_list):
         mask = full_schedule["night"] == night
-        
+
         # ignore nights that have no observations (bad weather/downtime)
         if not full_schedule[mask].empty:
-            night_lengths[i] = full_schedule[mask].iloc[-1]["observationStartMJD"] - full_schedule[mask].iloc[0]["observationStartMJD"]
+            night_lengths[i] = full_schedule[mask].iloc[-1]["observationStartMJD"]\
+                - full_schedule[mask].iloc[0]["observationStartMJD"]
 
     # get the first visit from each night
[…]

### 2022-08-26 lsst_detection_probability/detection_probability.py
update after run, move plotting code

@@ -227,3 +227,49 @@ def probability_from_id(hex_id, sorted_obs, distances, radial_velocities, first_
 
     # return the fraction of orbits that are findable
     return findable.astype(int).sum() / N_ORB
+
+
+def plot_LSST_schedule_with_orbits(schedule, reachable_schedule, orbits, night, colour_by="distance", lims="schedule"):
+    """Plot LSST schedule up using the dataframe containing fields. Each is assumed to be a circle of radius
+    2.1 degrees for simplicity.
+
+    Parameters
+    ----------
+    df : `pandas DataFrame`
+        DataFrame of fields (see `get_LSST_schedule`)
+    """
+    mask = orbits["night"] == night    
+    if len(mask[mask]) == 0:
+        print("Warning: No observations in this night")
+        return
+
+    fig, ax = plt.subplots(figsize=(20, 10))
+    
+    for table, colour, lw in zip([schedule, reachable_schedule], ["black", "tab:green"], [1, 2]):
+        ra_field, dec_field = table["fieldRA"][table["night"] == night], table["fieldDec"][table["night"] == night]
+        patches = [plt.Circle(center, 2.1) for center in np.transpose([ra_field, dec_field])]
+        coll = PatchCollection(patches, edgecolors=colour, facecolors="none", linewidths=lw)
+        ax.add_collection(coll)
+    
+    if colour_by == "orbit":
+        ax.scatter(orbits["RA_deg"][mask], orbits["Dec_deg"][mask], s=0.5, alpha=1, c=orbits["orbit_id"][mask])
+    elif colour_by == "distance":
+        scatter = ax.scatter(orbits["RA_deg"][mask], orbits["Dec_deg"][mask], s=0.5, alpha=1, c=orbits["r_au"][mask],
+                             norm=LogNorm(vmin=1e-1, vmax=2e1), cmap="magma")
+        fig.colorbar(scatter, label="Distance [AU]")
+    else:
+        raise ValueError("Invalid value for colour_by")
+    
+    ax.set_aspect("equal")
+
+    if lims in ["schedule", "reachable"]:
+        table = schedule if lims == "schedule" else reachable_schedule
+        ax.set_xlim(table[table["night"] == night]["fieldRA"].min() - 3, table[table["night"] == night]["fieldRA"].max() + 3)
[…]

### 2022-09-06 lsst_detection_probability/detection_probability.py
also mark fields with predicted detections

@@ -278,7 +278,8 @@ def first_last_pos_from_id(hex_id, sorted_obs, s3m_cart, distances, radial_veloc
     return ephemerides, truth
 
 
-def plot_LSST_schedule_with_orbits(schedule, reachable_schedule, ephemerides, truth, night,hex_id,
+def plot_LSST_schedule_with_orbits(schedule, reachable_schedule, ephemerides, joined_table,
+                                   truth, night, hex_id,
                                    colour_by="distance", lims="full_schedule", field_radius=2.1, s=10,
                                    filter_mask="all", show_mag_labels=False,
                                    fig=None, ax=None, show=True, ax_labels=True, cbar=True):
@@ -314,33 +315,39 @@ def plot_LSST_schedule_with_orbits(schedule, reachable_schedule, ephemerides, tr
         coll = PatchCollection(patches, edgecolors=colour, facecolors="none", linewidths=lw)
         ax.add_collection(coll)
 
-        # if we're doing the full schedule
+        # only do the following for the full schedule
         if colour == "black":
+            # annotate the number of fields in this night
             ax.annotate(f"{len(table[table_mask])} fields", xy=(0.98, 0.98), xycoords="axes fraction",
                         ha="right", va="top", fontsize=20)
 
+            # get the true observations for this night
             obs_dfs = [pd.read_hdf(f"../neocp/neo/filtered_visit_scores_{i:03d}.h5").sort_values("FieldMJD")[["FieldMJD", "night", "MaginFilter", "filter"]]
                for i in [0, 1]]
             all_obs = pd.concat(obs_dfs)
             all_obs.reset_index(inplace=True)
-            nightly_obs = all_obs[all_obs["night"] == night]
+            nightly_obs = all_obs[(all_obs["night"] == night) & (all_obs["hex_id"] == hex_id)]
 
+            # if there were observations on this night
             if not nightly_obs.empty:
-                det_times = nightly_obs[nightly_obs["hex_id"] == hex_id]["FieldMJD"].values
+                # work out in which fields the detections occurred
+                det_times = nightly_obs["FieldMJD"].values
+                field_times = table[table_mask]["observationStartMJD"]
+                ids = [(det_time - field_times[field_times <= det_time]).idxmin() for det_time in det_times]
+                det_fields = table.loc[ids]
 
-                if len(det_times) != 0:
[…]

### 2022-09-06 lsst_detection_probability/detection_probability.py
allow the use of predicted schedules for #20

@@ -30,7 +30,8 @@ def filter_tracklets(df, min_obs=2, min_arc=1, max_time=90):
                                   df["mjd_utc"].diff().min() * 1440 < max_time))
 
 
-def get_detection_probabilities(night_start, path="../neocp/neo/", detection_window=15, min_nights=3):
+def get_detection_probabilities(night_start, path="../neocp/neo/", detection_window=15, min_nights=3,
+                                schedule_type="predicted"):
     """Get the probability that LSST will detect each object that was observed in a particular night
 
     Parameters
@@ -53,13 +54,16 @@ def get_detection_probabilities(night_start, path="../neocp/neo/", detection_win
     """
     # create a list of nights in the detection window and get schedule for them
     night_list = list(range(night_start, night_start + detection_window))
-    schedule = get_LSST_schedule(night=(night_start, night_start + detection_window - 1))
+
+    if schedule_type == "predicted":
+        full_schedule = get_LSST_schedule(night=night_start, schedule_type=schedule_type)
+    else:
+        full_schedule = get_LSST_schedule(night=(night_start, night_start + detection_window - 1),
+                                          schedule_type=schedule_type)
 
     # offset the schedule by one row and re-merge to get the previous night column
-    shifted = schedule.shift()
-    shifted = shifted.drop("observationStartMJD", axis=1)
-    shifted = shifted.rename(columns={"night": "previousNight"})
-    full_schedule = pd.merge(schedule, shifted["previousNight"], left_index=True, right_index=True)
+    shifted = full_schedule.shift()
+    full_schedule["previousNight"] = shifted["night"]
 
     # calculate the length of each night in days
     night_lengths = np.zeros(detection_window)
@@ -182,6 +186,10 @@ def probability_from_id(hex_id, sorted_obs, distances, radial_velocities, first_
     bright_enough = joined_table["mag_in_filter"] < joined_table["fiveSigmaDepth"]
 
     joined_table["observed"] = np.logical_and(in_current_field, bright_enough)
+
+    # return if nothing got observed
+    if not joined_table["observed"].any():
+        return 0.0, joined_table
 
     # remove any nights that don't match requirements (min_obs, min_arc, max_time)
     df = joined_table[joined_table["observed"]]

### 2022-09-06 lsst_detection_probability/scheduling.py

@@ -20,7 +20,7 @@ params = {'figure.figsize': (12, 8),
 plt.rcParams.update(params)
 
 
-def get_LSST_schedule(night, night_zero=59638,
+def get_LSST_schedule(night, night_zero=59638, schedule_type="predicted",
                       fields=["fieldRA", "fieldDec", "observationStartMJD", "filter", "fiveSigmaDepth"]):
     """Get the schedule for LSST (where it will point at what time)
 
@@ -37,18 +37,37 @@ def get_LSST_schedule(night, night_zero=59638,
     df : `pandas DataFrame`
         DataFrame containing individual fields
     """
-    con = sqlite3.connect('/epyc/projects/jpl_survey_sim/10yrs/opsims/march_start_v2.1_10yrs.db')
-    cur = con.cursor()
 
-    if isinstance(night, int):
-        res = cur.execute(f"select {','.join(fields)} from observations where night={night + 1}")
+    if schedule_type == "actual":
+        con = sqlite3.connect('/epyc/projects/jpl_survey_sim/10yrs/opsims/march_start_v2.1_10yrs.db')
+        cur = con.cursor()
+
+        if isinstance(night, int):
+            res = cur.execute(f"select {','.join(fields)} from observations where night={night + 1}")
+        else:
+            res = cur.execute(f"select {','.join(fields)} from observations where night between {night[0] + 1} and {night[1] + 1}")
+        df = pd.DataFrame(res.fetchall(), columns=fields)
+
+        con.close()
+
+        df["night"] = (df["observationStartMJD"] - 0.5).astype(int) - night_zero
+    elif schedule_type == "predicted":
+        first_night = get_LSST_schedule(night=night, night_zero=night_zero,
+                                        schedule_type="actual", fields=fields)
+
+        con = sqlite3.connect(f'night{night + 1}_15days.db')
+        cur = con.cursor()
+        res = cur.execute(f"select {','.join(fields)} from observations where night between {night + 2} and {night + 15}")
+        rest = pd.DataFrame(res.fetchall(), columns=fields)
+
+        con.close()
+
+        rest["night"] = (rest["observationStartMJD"] - 0.5).astype(int) - night_zero
+
+        df = pd.concat([first_night, rest])
+        df.reset_index(inplace=True)
     else:
-        res = cur.execute(f"select {','.join(fields)} from observations where night between {night[0] + 1} and {night[1] + 1}")
[…]

### 2022-09-06 lsst_detection_probability/detection_probability.py
switch to using SkyCoord.separation as part of #22

@@ -179,13 +179,19 @@ def probability_from_id(hex_id, sorted_obs, distances, radial_velocities, first_
                                                              asteroid_type="C")
     joined_table["mag_in_filter"] = mag_in_filter
 
-    # mask those that are within the field (2.1 degrees)
-    in_current_field = np.sqrt((joined_table["fieldRA"] - joined_table["RA_deg"])**2
-                               + (joined_table["fieldDec"] - joined_table["Dec_deg"])**2) <= 2.1
-
+    # work out which are bright enough to be detected
     bright_enough = joined_table["mag_in_filter"] < joined_table["fiveSigmaDepth"]
 
-    joined_table["observed"] = np.logical_and(in_current_field, bright_enough)
+    # of those, find those which are roughly within the field (2.1 degrees)
+    # operating on a subset because SkyCoord gets slow for large datasets
+    in_current_field = np.repeat(False, len(joined_table))
+    bright_table = joined_table[bright_enough]
+    obj_pos = SkyCoord(ra=bright_table["RA_deg"], dec=bright_table["Dec_deg"], unit="degree", frame="icrs")
+    sch_pos = SkyCoord(ra=bright_table["fieldRA"], dec=bright_table["fieldDec"], unit="degree", frame="icrs")
+    in_current_field[bright_enough] = obj_pos.separation(sch_pos) <= 2.1 * u.deg
+
+    # combine the masks into a single observed boolean
+    joined_table["observed"] = np.logical_and(bright_enough, in_current_field)
 
     # return if nothing got observed
     if not joined_table["observed"].any():

### 2022-09-06 lsst_detection_probability/detection_probability.py
adjust radial velocity range for #22

@@ -96,8 +96,8 @@ def get_detection_probabilities(night_start, path="../neocp/neo/", detection_win
     probs = np.zeros(len(unique_objs))
     for i, hex_id in enumerate(unique_objs):
         start = time.time()
-        probs[i], _ = probability_from_id(hex_id, sorted_obs, distances=np.logspace(-1, 1, 50) * u.AU,
-                                          radial_velocities=np.linspace(-100, 100, 20) * u.km / u.s,
+        probs[i], _ = probability_from_id(hex_id, sorted_obs, distances=np.logspace(-1, 1, 51) * u.AU,
+                                          radial_velocities=np.linspace(-50, 10, 21) * u.km / u.s,
                                           first_visit_times=first_visit_times, full_schedule=full_schedule,
                                           night_lengths=night_lengths, night_list=night_list,
                                           detection_window=detection_window, min_nights=min_nights)

### 2022-09-14 lsst_detection_probability/variant_orbits.py
handle case with `only_neos=True` and `H=None`

@@ -183,7 +183,7 @@ def variant_orbit_ephemerides(ra, dec, ra_end, dec_end, delta_t, obstime, distan
         perihelion = orbits_class.keplerian[:, 0] * (1 - orbits_class.keplerian[:, 1])
         orbits_class = thor.Orbits(orbits=corrected_orbits[perihelion < 1.3],
                                    epochs=Time(corrected_t0[perihelion < 1.3], format="mjd"),
-                                   H=H[perihelion < 1.3])
+                                   H=H[perihelion < 1.3] if H is not None else H)
 
     # default to one day after the observation
     if eph_times is None:

### 2022-12-07 hybridcat/hybridcat/pipeline.py
latest difi discussion things

@@ -176,7 +176,8 @@ class HybridCreator():
             print("Building hybrid catalogue")
 
         # convert both catalogues to cometary coordinates
-        self.transform_both_to_cometary()
+        # HACK: Don't do this because OpenOrb has that stupid bug
+        # self.transform_both_to_cometary()
 
         if self.verbose:
             print("Both catalogues transformed back to cometary")

### 2022-12-07 lsst_detection_probability/detection_probability.py

@@ -407,7 +407,7 @@ def plot_LSST_schedule_with_orbits(schedule, reachable_schedule, ephemerides, jo
         return None, None
 
     # plot each schedule with difference colours and widths
-    for table, colour, lw in zip([schedule, reachable_schedule], ["black", "tab:green"], [1, 2]):
+    for table, colour, lw in zip([schedule, reachable_schedule], ["black", "#000000"], [1, 1]):
         # ensure you only get the current night
         table_mask = table["night"] == night
 

### 2022-12-07 lsst_detection_probability/variant_orbits.py

@@ -120,6 +120,7 @@ def variant_orbit_ephemerides(ra, dec, ra_end, dec_end, delta_t, obstime, distan
             ra = np.repeat(ra.value, repeats=size) * ra.unit
             ra_end = np.repeat(ra_end.value, repeats=size) * ra_end.unit
         else:
+            # TODO: check with Mario about adding scatter near poles
             ra = np.random.normal(ra.value, scale=sigma_ra.to(ra.unit).value, size=size) * ra.unit
             ra_end = np.random.normal(ra_end.value, scale=sigma_ra.to(ra_end.unit).value, size=size) * ra_end.unit
 

### 2022-12-07 neocp/difi_combiner.py

@@ -1,0 +1,29 @@
+import pandas as pd
+import h5py as h5
+import numpy as np
+
+all_ids = np.array([])
+all_nfs = np.array([])
+
+for i in range(3637):
+    # get this night's values
+    this_ids = np.load(f"difi_MBAs_ids_{i:04d}.npy")
+    this_nfs = np.load(f"difi_MBAs_ids_{i:04d}.npy")
+    
+    # combine it with the previous nights'
+    all_ids = np.concatenate([all_ids, this_ids])
+    all_nfs = np.concatenate([all_nfs, this_nfs])
+
+    # sort everything by the night on which it was found
+    order = np.argsort(all_night_found)
+    all_ids = all_ids[order]
+    all_night_found = all_night_found[order]
+
+    # get only the unique ids and the corresponding nights
+    all_ids, idx = np.unique(all_ids, return_index=True)
+    all_night_found = all_night_found[idx]
+
+    print(i)
+
+np.save("all_obj_ids.npy", all_ids)
+np.save("all_night_found.npy", all_night_found)

### 2022-12-07 neocp/difi_runner.py

@@ -1,20 +1,9 @@
+import difi
+
 import pandas as pd
-from astropy.coordinates import Angle, SkyCoord
-from astropy.time import Time
-import astropy.units as u
 import numpy as np
-from os import listdir
-from os.path import isfile
+
 import argparse
-import time
-from multiprocessing import Pool
-from itertools import repeat
-import subprocess
-
-
-def print_time_delta(start, end, label):
-    delta = end - start
-    print(f"  {int(delta // 60):02d}m{int(delta % 60):02d}s - ({label})")
 
 
 f2n = [[0, 1, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19],
@@ -242,298 +231,61 @@ def find_last_file(night_range):
                 file = i
     return file
 
-
-def split_observations(obs, n_cores=28):
-    """Split observations over many cores but keep groups of tracklets together so that they get masked
-    correctly!
-
-    Parameters
-    ----------
-    obs : `pandas.DataFrame`
-        Observation table
-    n_cores : `int`, optional
-        Number of cores to split over, by default 28
-
-    Returns
-    -------
-    split_obs : `list`
-        List of dataframes with length `n_cores` and each with size approximately `len(obs) / n_cores`
-    """
-    indices = np.array([None for _ in range(n_cores - 1)])
-    i, cursor, dx = 0, 0, len(obs) // n_cores
-    ids = obs["ObjID"].values
-
-    while i < n_cores - 1:
-        cursor += dx
-        while ids[cursor] == ids[cursor + 1]:
-            cursor += 1
-        indices[i] = cursor
-        i += 1
-
-    return np.split(obs, indices)
+def night_found(obs_ids, observations, column_mapping):
+    return np.unique(observations.loc[obs_ids][column_mapping["night"]].values)[2]
 
 
-def filter_observations(df, min_obs=2, min_arc=1, max_time=90):
-    # create a mask based on min # of obs, min arc length, max time between shortest pair
-    mask = df.groupby(["ObjID", "night"]).apply(filter_tracklets, min_obs, min_arc, max_time)
+def cla():
+    parser = argparse.ArgumentParser(description='Run difi on a window of MBA observations')
+    parser.add_argument('-s', '--start', default=0, type=int,
+                        help='Start night of window')
+    parser.add_argument('-w', '--window', default=15, type=int,
+                        help='Length of detection window')
[…]

### 2023-02-05 lsst_detection_probability/detection_probability.py
remove stuff after porting

@@ -1,563 +1,0 @@
-import astropy.units as u
-from astropy.time import Time
-from astropy.coordinates import SkyCoord
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.colors import BoundaryNorm
-from matplotlib.collections import PatchCollection
-import time
-
-from rubin_sim.utils import LsstCameraFootprint
-import os.path
-
-from multiprocessing import Pool
-from functools import partial
-
-from collections import defaultdict
-
-import thor
-from thor.backend import PYOORB
-backend = PYOORB()
-
-from variant_orbits import variant_orbit_ephemerides
-from scheduling import get_LSST_schedule
-from magnitudes import convert_colour_mags
-
-import sys
-sys.path.append("../neocp")
-from lsst_neocp import find_first_file, find_last_file
-
-
-def filter_tracklets(df, min_obs=2, min_arc=1, max_time=90):
-    init = SkyCoord(ra=df["RA_deg"].iloc[0], dec=df["Dec_deg"].iloc[0], unit="deg")
-    final = SkyCoord(ra=df["RA_deg"].iloc[-1], dec=df["Dec_deg"].iloc[-1], unit="deg")
-
-    return np.logical_and.reduce((len(df) >= min_obs,
-                                  init.separation(final).to(u.arcsecond).value > min_arc,
-                                  df["mjd_utc"].diff().min() * 1440 < max_time))
-
-
-def get_detection_probabilities(night_start, obj_type="neo", detection_window=15, min_nights=3,
-                                schedule_type="predicted", pool_size=48, save_results=True):
-    """Get the probability that LSST will detect each object that was observed in a particular night
-
-    Parameters
-    ----------
-    night_start : `int`
-        Night of the initial observations
-    obj_type : `str`, optional
-        Object type used to get/set paths to file, by default "neo", other option is "mba"
-    detection_window : `int`, optional
-        How many days in the detection window, by default 15
-    min_nights : `int`, optional
-        Minimum number of nights on which observations need to have occurred, by default 3
-    pool_size : `int`, optional
-        How many workers to put in the multiprocessing pool, by default 48
-    save_results : `bool`, optional
-        Whether to save the results to a file, by default True
-
-    Returns
-    -------
-    probs : `list`
-        Estimated probability that each object will be detected by LSST alone
-    unique_objs : `list`
-        List of unique hex ids that have digest2 > 65 that were observed on `night_start`
-    """
-    start = time.time()
-    lap = time.time()
[…]

### 2023-02-05 lsst_detection_probability/findable_tables.py

@@ -1,60 +1,0 @@
-import numpy as np
-import pandas as pd
-import difi
-import time
-
-def create_findable_obs_tables(obj_type="neo", min_nights=3, detection_window=15, file_ids=range(24)):
-    print("Let the games begin...")
-    start = time.time()
-
-    # get all of the observations
-    obs_dfs = [pd.read_hdf(f"../neocp/{obj_type}/filtered_visit_scores_{i:03d}.h5").sort_values("FieldMJD")[["FieldMJD", "night"]]
-                for i in file_ids]
-    all_obs = pd.concat(obs_dfs)
-    all_obs["obs_id"] = np.arange(len(all_obs))
-    all_obs.reset_index(inplace=True)
-
-    print(f"Obs file done, {time.time() - start:1.1f}s elapsed")
-    obs_done = time.time()
-
-    # run difi
-    _, findable_obs, _ = difi.analyzeObservations(
-        observations=all_obs,
-        classes=None,
-        metric="nightly_linkages",
-        column_mapping={"obs_id": "obs_id", "truth": "hex_id", "night": "night", "time": "FieldMJD"}
-    )
-
-    print(f"Difi done, {time.time() - obs_done:1.1f}s elapsed")
-    difi_done = time.time()
-
-    # hack around difi to check if the window is actually satisfied and on which night it is first detected
-    findable_obs["night_detected"] = np.zeros(len(findable_obs)).astype(int)
-    findable_obs["actually_findable"] = np.repeat(True, len(findable_obs))
-
-    for ind, row in findable_obs.iterrows():
-        obs_nights = np.unique(all_obs.loc[row["obs_ids"]]["night"].values)
-        diff_nights = np.diff(obs_nights)
-        window_sizes = np.array([sum(diff_nights[i:i + min_nights - 1])
-                                for i in range(len(diff_nights) - min_nights + 2)])
-
-        # record whether any are short enough
-        if np.any(window_sizes <= detection_window):
-            detection_obs_ind = np.arange(len(window_sizes))[window_sizes <= detection_window][0] + min_nights - 1
-            findable_obs.loc[ind, "night_detected"] = obs_nights[detection_obs_ind]
-        else:
-            findable_obs.loc[ind, "night_detected"] = -1
-            findable_obs.loc[ind, "actually_findable"] = False
-
[…]

### 2023-02-05 lsst_detection_probability/magnitudes.py

@@ -1,147 +1,0 @@
-import numpy as np
-
-
-def absolute_magnitude(m, d_ast_sun, d_ast_earth, d_earth_sun=None, phase_angle=None, G=0.15):
-    """Get the absolute magnitude of an asteroid (following MPC equation
-    https://minorplanetcenter.net/iau/ECS/MPCArchive/1985/MPC_19851227.pdf)
-
-    Parameters
-    ----------
-    m : `float/array`
-        Apparent magnitude
-    d_ast_sun : `float/array`
-        Distance from the asteroid to the Sun in AU
-    d_ast_earth : `float/array`
-        Distance from the asteroid to the Earth in AU
-    d_earth_sun : `float/array`
-        Distance from the Earth to the Sun in AU, optional. Must be supplied if `phase_angle` is None.
-    phase_angle : `float/array`
-        Phase angle in radians, optional. Must be supplied if `d_earth_sun` is None.
-    G : `float/array`
-        Slope parameter, optional. By default, 0.15.
-
-    Returns
-    -------
-    H : `float/array`
-        Absolute magnitude
-    """
-    if phase_angle is None and d_earth_sun is None:
-        raise ValueError("Either `phase_angle` or `d_earth_sun` must be provided")
-    elif phase_angle is None:
-        phase_angle = np.arccos((d_ast_sun**2 + d_ast_earth**2 - d_earth_sun**2)
-                                / (2 * d_ast_sun * d_ast_earth))
-    return m - 5 * np.log10(d_ast_sun * d_ast_earth)\
-        + 2.5 * np.log10((1 - G) * phi(1, phase_angle) + G * phi(2, phase_angle))
-
-
-def apparent_magnitude(H, d_ast_sun, d_ast_earth, d_earth_sun=None, phase_angle=None, G=0.15):
-    """Get the apparent magnitude of an asteroid (following MPC equation
-    https://minorplanetcenter.net/iau/ECS/MPCArchive/1985/MPC_19851227.pdf)
-
-    Parameters
-    ----------
-    H : `float/array`
-        Absolute magnitude
-    d_ast_sun : `float/array`
-        Distance from the asteroid to the Sun in AU
-    d_ast_earth : `float/array`
-        Distance from the asteroid to the Earth in AU
-    d_earth_sun : `float/array`
-        Distance from the Earth to the Sun in AU, optional. Must be supplied if `phase_angle` is None.
-    phase_angle : `float/array`
[…]

### 2023-02-05 lsst_detection_probability/predicted_schedules/get_schedules.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-
-FILES_TO_COPY=""
-for i in {1..365}
-do
-    FILES_TO_COPY+="/gscratch/scrubbed/yoachim/survey_predicted/night${i}_15days.db "
-done
-
-echo $FILES_TO_COPY
-
-scp tomwagg@mox.hyak.uw.edu:"$FILES_TO_COPY" .

### 2023-02-05 lsst_detection_probability/run.py

@@ -1,12 +1,0 @@
-from detection_probability import get_detection_probabilities
-import time
-
-run_start = time.time()
-
-for i in range(291, 365):
-    print(f"\nStarting night {i}")
-    start = time.time()
-    get_detection_probabilities(night_start=i, obj_type="mba")
-    print(f"Time for this run: {time.time() - start:1.1f}s")
-
-print(f"\n\nOverall, it took {time.time() - run_start:1.1f}s")

### 2023-02-05 lsst_detection_probability/scheduling.py

@@ -1,100 +1,0 @@
-import sqlite3
-import pandas as pd
-import matplotlib.pyplot as plt
-
-plt.rc('font', family='serif')
-plt.rcParams['text.usetex'] = False
-fs = 24
-
-# update various fontsizes to match
-params = {'figure.figsize': (12, 8),
-          'legend.fontsize': fs,
-          'axes.labelsize': fs,
-          'xtick.labelsize': 0.6 * fs,
-          'ytick.labelsize': 0.6 * fs,
-          'axes.linewidth': 1.1,
-          'xtick.major.size': 7,
-          'xtick.minor.size': 4,
-          'ytick.major.size': 7,
-          'ytick.minor.size': 4}
-plt.rcParams.update(params)
-
-
-def get_LSST_schedule(night, night_zero=59638, schedule_type="predicted",
-                      fields=["fieldRA", "fieldDec", "observationStartMJD",
-                              "filter", "fiveSigmaDepth", "rotSkyPos"]):
-    """Get the schedule for LSST (where it will point at what time)
-
-    Parameters
-    ----------
-    night : `int`
-        Which night you want the schedule for
-    fields : `list`, optional
-        Fields you want from the database, by default ["fieldRA", "fieldDec", "observationStartMJD",
-        "filter", "fiveSigmaDepth", "rotSkyPos"]
-
-    Returns
-    -------
-    df : `pandas DataFrame`
-        DataFrame containing individual fields
-    """
-
-    if schedule_type == "actual":
-        con = sqlite3.connect('/epyc/projects/jpl_survey_sim/10yrs/opsims/march_start_v2.1_10yrs.db')
-        cur = con.cursor()
-
-        if isinstance(night, int):
-            res = cur.execute(f"select {','.join(fields)} from observations where night={night + 1}")
-        else:
-            res = cur.execute(f"select {','.join(fields)} from observations where night between {night[0] + 1} and {night[1] + 1}")
-        df = pd.DataFrame(res.fetchall(), columns=fields)
-
-        con.close()
-
-        df["night"] = (df["observationStartMJD"] - 0.5).astype(int) - night_zero
-    elif schedule_type == "predicted":
-        first_night = get_LSST_schedule(night=night, night_zero=night_zero,
-                                        schedule_type="actual", fields=fields)
-
[…]

### 2023-02-05 lsst_detection_probability/variant_orbits.py

@@ -1,302 +1,0 @@
-import astropy.units as u
-from astropy.time import Time
-from astropy.coordinates import SkyCoord, EarthLocation, get_sun
-from astropy.visualization import quantity_support
-quantity_support()
-
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.colors import LogNorm
-import pandas as pd
-pd.set_option("display.max_columns", None)
-
-from magnitudes import absolute_magnitude
-
-import thor
-from thor.constants import Constants
-from thor.backend import PYOORB
-backend = PYOORB()
-
-import urllib.request
-import json
-
-plt.rc('font', family='serif')
-plt.rcParams['text.usetex'] = False
-fs = 24
-
-# update various fontsizes to match
-params = {'figure.figsize': (12, 8),
-          'legend.fontsize': fs,
-          'axes.labelsize': fs,
-          'xtick.labelsize': 0.6 * fs,
-          'ytick.labelsize': 0.6 * fs,
-          'axes.linewidth': 1.1,
-          'xtick.major.size': 7,
-          'xtick.minor.size': 4,
-          'ytick.major.size': 7,
-          'ytick.minor.size': 4}
-plt.rcParams.update(params)
-
-
-def variant_orbit_ephemerides(ra, dec, ra_end, dec_end, delta_t, obstime, distances, radial_velocities,
-                              sigma_ra=0.1 * u.arcsecond, sigma_dec=0.1 * u.arcsecond, apparent_mag=None,
-                              eph_times=None, coords="heliocentriceclipticiau76", location="Gemini South",
-                              obs_code="I11", pm_ra_cosdec=None, pm_dec=None, only_neos=False, verbose=False,
-                              num_jobs="auto", chunk_size=100):
-    """Generate ephemerides for a series of variant orbits for an observed object without constraints on its
-    distance and radial velocity.
-
-    Parameters
-    ----------
-    ra : `float`
-        Right ascension at initial observation (with Astropy units)
-    dec : `float`
-        Declination at initial observation (with Astropy units)
-    obstime : `Astropy Time object`
-        Time of initial observation
-    ra_end : `float`
-        Right ascension at final observation (with Astropy units)
-    dec_end : `float`
-        Declination at final observation (with Astropy units)
-    delta_t : `Astropy Time object`
-        Time between observations
-    pm_ra_cosdec : `float`, optional
[…]

### 2023-02-05 neocp/difi_combiner.py

@@ -1,29 +1,0 @@
-import pandas as pd
-import h5py as h5
-import numpy as np
-
-all_ids = np.array([])
-all_nfs = np.array([])
-
-for i in range(3637):
-    # get this night's values
-    this_ids = np.load(f"difi_MBAs_ids_{i:04d}.npy")
-    this_nfs = np.load(f"difi_MBAs_ids_{i:04d}.npy")
-
-    # combine it with the previous nights'
-    all_ids = np.concatenate([all_ids, this_ids])
-    all_nfs = np.concatenate([all_nfs, this_nfs])
-
-    # sort everything by the night on which it was found
-    order = np.argsort(all_nfs)
-    all_ids = all_ids[order]
-    all_nfs = all_nfs[order]
-
-    # get only the unique ids and the corresponding nights
-    all_ids, idx = np.unique(all_ids, return_index=True)
-    all_nfs = all_nfs[idx]
-
-    print(i)
-
-np.save("all_obj_ids.npy", all_ids)
-np.save("all_night_found.npy", all_nfs)

### 2023-02-05 neocp/difi_runner.py

@@ -1,291 +1,0 @@
-import difi
-
-import pandas as pd
-import numpy as np
-
-import argparse
-
-
-f2n = [[0, 1, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19],
-       [19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31],
-       [31, 35, 36, 37, 39, 40, 41, 42, 43, 44, 45, 46],
-       [46, 47, 49, 50, 52, 53, 54, 56, 57, 58, 59, 60, 61],
-       [61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71, 72],
-       [72, 73, 74, 75, 76, 77, 78, 79, 82, 83, 85, 86, 87, 88, 89],
-       [89, 90, 91, 93, 94, 95, 98, 107, 108, 109, 110, 111, 112],
-       [112, 113, 114, 115, 118, 119, 121, 122, 124, 128, 129, 130, 131, 132],
-       [132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144],
-       [144, 145, 146, 147, 148, 149, 150, 151, 152, 154, 157, 159],
-       [159, 160, 161, 162, 163, 165, 166, 167, 168, 169, 170, 171],
-       [171, 172, 173, 174, 175, 178, 179, 180, 181, 182, 183, 184, 185],
-       [185, 186, 187, 188, 191, 192, 193, 196, 197, 198, 199, 200, 201, 202],
-       [202, 203, 204, 205, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224],
-       [224, 225, 226, 227, 228, 229, 230, 231, 232, 234, 235, 236, 237, 238, 239],
-       [239, 240, 242, 243, 244, 245, 246, 247, 255, 256, 257, 258, 259, 260],
-       [260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270, 271, 272, 273, 274, 275],
-       [275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285, 286, 287, 288, 289],
-       [289, 290, 291, 292, 293, 294, 295, 296, 297, 298, 299, 303, 304, 305, 306, 307, 308],
-       [308, 309, 310, 311, 312, 313, 314, 315, 316, 317, 318, 319, 320, 321, 322],
[…]

### 2023-02-05 neocp/helpers.py

@@ -1,80 +1,0 @@
-import matplotlib.pyplot as plt
-from matplotlib.patches import Patch
-import numpy as np
-import pandas as pd
-from os import listdir
-from os.path import isfile
-
-plt.rc('font', family='serif')
-plt.rcParams['text.usetex'] = False
-fs = 24
-
-# update various fontsizes to match
-params = {'figure.figsize': (12, 8),
-          'legend.fontsize': fs,
-          'axes.labelsize': fs,
-          'xtick.labelsize': 0.6 * fs,
-          'ytick.labelsize': 0.6 * fs,
-          'axes.linewidth': 1.1,
-          'xtick.major.size': 7,
-          'xtick.minor.size': 4,
-          'ytick.major.size': 7,
-          'ytick.minor.size': 4}
-plt.rcParams.update(params)
-
-
-def plot_neo_scores(neo_scores, density=False, bins=np.linspace(0, 100, 30), night=0):
-    fig, ax = plt.subplots(figsize=(12, 8))
-
-    handles = []
-
-    for score in neo_scores:
-        ax.hist(score["scores"], bins=bins, facecolor=score["colour"][:-1] + [0.2],
-                label=score["label"], lw=3, density=density)
-        ax.hist(score["scores"], bins=bins, color=score["colour"], histtype="step",
-                lw=3, density=density)
-
-        handles.append(Patch(facecolor=score["colour"][:-1] + [0.2],
-                             edgecolor=score["colour"],
-                             label=score["label"], lw=3))
-
-    ax.legend(handles=handles, loc="upper center", ncol=2, fontsize=0.8 * fs)
-
-    ax.set_xlabel("NEO Score")
-
-    if density:
-        ax.set_ylabel("Density")
-    else:
-        ax.set_ylabel("Number of objects")
-
-    ax.set_title(f"Night {night}", fontsize=fs)
-
-    return fig, ax
-
-
-def get_specific_neo_score(path, file_name):
-    if file_name.endswith(".filtered.dat"):
-        if isfile(path + file_name):
-            with open(path + file_name, "r") as f:
-                ignore_me = f.readline().rstrip() == ""
-            if not ignore_me:
-                df = pd.read_fwf(path + file_name)
-                return df["NEO"].values, df["Desig."].values
-
-    return None, None
-
-
-def get_neo_scores(path, night=None):
-    if night is None:
-        neo_scores = np.array([])
-        ids = np.array([])
-        files = listdir(path)
-
[…]

### 2023-02-05 neocp/lsst_neocp.py

@@ -1,539 +1,0 @@
-import pandas as pd
-from astropy.coordinates import Angle, SkyCoord
-from astropy.time import Time
-import astropy.units as u
-import numpy as np
-from os import listdir
-from os.path import isfile
-import argparse
-import time
-from multiprocessing import Pool
-from itertools import repeat
-import subprocess
-
-
-def print_time_delta(start, end, label):
-    delta = end - start
-    print(f"  {int(delta // 60):02d}m{int(delta % 60):02d}s - ({label})")
-
-
-f2n = [[0, 1, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19],
-       [19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31],
-       [31, 35, 36, 37, 39, 40, 41, 42, 43, 44, 45, 46],
-       [46, 47, 49, 50, 52, 53, 54, 56, 57, 58, 59, 60, 61],
-       [61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71, 72],
-       [72, 73, 74, 75, 76, 77, 78, 79, 82, 83, 85, 86, 87, 88, 89],
-       [89, 90, 91, 93, 94, 95, 98, 107, 108, 109, 110, 111, 112],
-       [112, 113, 114, 115, 118, 119, 121, 122, 124, 128, 129, 130, 131, 132],
-       [132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144],
-       [144, 145, 146, 147, 148, 149, 150, 151, 152, 154, 157, 159],
-       [159, 160, 161, 162, 163, 165, 166, 167, 168, 169, 170, 171],
-       [171, 172, 173, 174, 175, 178, 179, 180, 181, 182, 183, 184, 185],
-       [185, 186, 187, 188, 191, 192, 193, 196, 197, 198, 199, 200, 201, 202],
-       [202, 203, 204, 205, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224],
-       [224, 225, 226, 227, 228, 229, 230, 231, 232, 234, 235, 236, 237, 238, 239],
[…]

### 2023-02-05 neocp/neo/convert.sh

@@ -1,6 +1,0 @@
-for i in $(seq 0 199)
-do
-   printf -v two "%02d" $i
-   printf -v three "%03d" $i
-   mv night_${two}.filtered.dat night_${three}.filtered.dat
-done

### 2023-02-05 scratch/pools.py

@@ -1,26 +1,0 @@
-# import numpy as np
-# from detection_probability import get_detection_probabilities
-
-# probs, unique_objs = get_detection_probabilities(10)
-# np.save("probs_pool_test.npy", probs)
-
-# print("NOICE")
-
-# with Pool(32) as pool:
-#         probs = pool.map(partial(probability_from_id, sorted_obs=sorted_obs,
-#                                  distances=np.logspace(-1, 1, 50) * u.AU,
-#                                  radial_velocities=np.linspace(-100, 100, 20) * u.km / u.s,
-#                                  first_visit_times=first_visit_times, full_schedule=full_schedule,
-#                                  night_lengths=night_lengths, night_list=night_list,
-#                                  detection_window=detection_window, min_nights=min_nights), unique_objs)
-
-import astropy.units as u
-import numpy as np
-from multiprocessing import Pool
-from functools import partial
-def mult(x, y, z):
-    print(x, y, z)
-    return x * y * z
-with Pool(5) as p:
-    x = p.map(partial(mult, y=7, z=2), [1, 2, 3])
-    print(x)
